### 2024-03-07 SRC/Data_Prep/Data_prep.Rmd
started fixing the merge mistakes and seperated files

# Cleaning the Data
movie_data <- read_csv(movie_data)

So after retrieving and mergig our data directly form the IMBD site, we now need to chcek and clean the data. In this markdown the data set is cleaned, reformatted and restructured.

```{r libraries, message=FALSE, warning=FALSE}
install(tidyverse)
library(tidyverse)
```

First, let's think about some operalization basics. Or more specifically, the operalization of our variables.

# starting with out DV: ratings
```{r Raw DV print}
print(summary(movie_data$averageRating))
```

Okay. So the scale is okay BUT remember that these are AVERAGE ratings, and that on average ratings 1 and 10 are quite extreem and frankly, unrealistic.

let's visualize how ratings are distributed

```{r DV plots, message=FALSE, warning=FALSE}
ggplot((movie_data), aes(x = averageRating)) +
  geom_histogram(binwidth = 1, fill = "darkorange", color = "black") +
  labs(title = "Distribution of averageRating",
       x = "Average Rating",y = "Frequency") +
  scale_x_continuous(breaks = seq(0, 10, by = 1)) +  
  theme_minimal()
```

```{r}
ggplot(movie_data, aes(x = averageRating)) +
  geom_histogram(binwidth = 0.1, fill = "orange", color = "black") +
  scale_x_continuous(breaks = seq(0, 10, by = 0.5), limits = c(0, 10), labels = scales::number_format(accuracy = 0.1)) +
  labs(x = "averageRating", y = "Frequency") +
  theme_minimal()
```
As you can see there appears to be a normal distribution that is slightly skewed to the left.
If you think logically about this this may be a result from the number of reviews given as opposed to the actual rating

```{r DV vs NumVotes, message=FALSE, warning=FALSE}
print(summary(movie_data$numVotes))
```

Do you see how the average movie only has 106 votes? Or even 5! that will defiantely influence the average

```{r Plot DV and numVotes, message=FALSE, warning=FALSE}
ggplot(movie_data, aes(x = numVotes)) +
  geom_dotplot(fill = "darkorange", color = "black", binwidth = 500) +
  labs(title = "Distribution of numVotes",
       x = "Number of Votes", y = "Frequency") + 
  theme_minimal()

movie_data$numVotes_group <- cut(movie_data$numVotes, breaks = c(-Inf, 50, Inf), labels = c("Below 50", "Above 50"))
print(table(movie_data$numVotes_group))
````

Okay, so let's filter some of there observations out. These observations are not deleted. But they are simply left behind in the corner. We want reliable data and these observation are unlikely to be reliable. But instead of arbritarily unselecting stuff we should plot the data and see where some issues lie.

```{r Filtering DV, message=FALSE, warning=FALSE}

below_100 <- movie_data %>%
  select(numVotes) %>%
  filter(numVotes < 100)

ggplot(below_100, aes(x = numVotes)) +
  geom_histogram() +
  labs(title = "Distribution of numVotes Below 100",
       x = "Group (Interval of 10)", y = "Number of Votes") +
  theme_minimal()
```

So as you may have seen these observation are heavily left skewed. So we are indeed likely to get these extreme average rating value's from the observations that have very few number of ratings.

Let's filter these observations out now.

### 2024-03-07 SRC/Data_Prep/Data_prep.Rmd
updated structure by reformatting files

@@
 # Cleaning the Data
-movie_data <- read_csv(movie_data)
-
 So after retrieving and mergig our data directly form the IMBD site, we now need to chcek and clean the data. In this markdown the data set is cleaned, reformatted and restructured.
@@
 library(tidyverse)
+```
+
+```{r reformatting the data, message=FALSE, warning=FALSE}
+movie_data <- read_csv(movie_data)
+
+movie_data <- movie_data %>%
+  mutate(across(c(tconst, directors, writers, titleType, isAdult,genres, parentTconst,region,language,isOriginalTitle), as.factor)) %>%
+  mutate(across(c(averageRating,numVotes,runtimeMinutes, title,seasonNumber, episodeNumber), as.numeric)) %>%
+  mutate(across(c(primaryTitle, originalTitle,types, attributes),as.string))
 ```
@@
 Let's filter these observations out now.
+
+```{r}
+movie_data <- movie_data %>%
+  filter(numVotes > 100) 
+```
+
+# IV data_set
+
+Now that we have clean

### 2024-03-07 SRC/Data_Prep/Data_prep.R

@@ -1,0 +1,46 @@
+#Now let's think about some operalization basics. Or more specifically, the operalization of our variables.
+
+#starting with out DV: ratings
+print(summary(movie_data$averageRating))
+
+#Okay. So the scale is okay BUT remember that these are AVERAGE ratings, and that on average ratings 1 and 10 are quite extreem and frankly, unrealistic.
+#let's visualize how ratings are distributed
+
+ggplot(movie_data), aes(x = averageRating)) +
+  geom_histogram(binwidth = 1, fill = "darkorange", color = "black") +
+  labs(title = "Distribution of averageRating",
+       x = "Average Rating",y = "Frequency") +
+  scale_x_continuous(breaks = seq(0, 10, by = 1)) +  
+  theme_minimal()
+
+ggplot(movie_data, aes(x = averageRating)) +
+  geom_histogram(binwidth = 0.1, fill = "orange", color = "black") +
+  scale_x_continuous(breaks = seq(0, 10, by = 0.5), limits = c(0, 10), labels = scales::number_format(accuracy = 0.1)) +
+  labs(x = "averageRating", y = "Frequency") +
+  theme_minimal()
+
+#as you can see there appears to be a normal distribution that is slightly skewed to the left.
+#If you think logically about this this may be a result from the number of reviews given as opposed to the actual rating
+
+print(summary(movie_data$numVotes))
+
+#do you see how tha average movie only has 106 votes? Or even 5! that will defiantely influence the average 
+ggplot(movie_data, aes(x = numVotes)) +
+  geom_dotplot(fill = "darkorange", color = "black", binwidth = 500) +
+  labs(title = "Distribution of numVotes",
+       x = "Number of Votes", y = "Frequency") + 
+  theme_minimal()
+
+movie_data$numVotes_group <- cut(movie_data$numVotes, breaks = c(-Inf, 50, Inf), labels = c("Below 50", "Above 50"))
+print(table(movie_data$numVotes_group))
+
+
+below_100 <- movie_data %>%
+  select(numVotes) %>%
+  filter(numVotes < 100)
+
+ggplot(below_100, aes(x = numVotes)) +
+  geom_histogram() +
+  labs(title = "Distribution of numVotes Below 100",
+       x = "Group (Interval of 10)", y = "Number of Votes") +
+  theme_minimal()

### 2024-03-13 SRC/analysis/regression_analysis.Rmd
regression analysis and data_clean alterations

# Let's run our analysis! 
## And see how genre prefferences as inferred from average ratings evolve over time

```{r libraries, message=FALSE, warning=FALSE}

install.packages("tidyverse")
install.packages("fixest")
install.packages("tidyr")
install.packages("skimr")
install.packages("infer")
install.packages("modelsummary")
install.packages("broom")
install.packages("purrr")
install.packages("estmatr")
install.packages("pdftools")

library(tidyverse)
library(fixest)
library(tidyr)
library(skimr)
library(infer)
library(modelsummary)
library(broom)
library(purrr)
library(viridis)
library(estimatr)
library(pdftools)
```

Let's start with loading the data 
```{ r input}
mdc <- read_csv("movie_data_cleaned.csv")

```

## basic skeleton model
Let's start with a simple skeleton model and build it from there in gradual steps.So the most basic form is start regression all our genres on the average rating. So let's do that!

```{r skeleton model}

simple_model <- feols(averageRating ~ drama + romance + war + crime + thriller+ history + comedy + fantasy + adventure + mystery + biography + action + scifi + western + horror + sport + documentary + musical + filmnoir + animation + adult + gameshow + realitytv + talkshow + short + news,
                      data = movie_data_test,
                      split = ~ slide_window_5)
summary(simple_model)

```
So we now have the most basic form of a regression to work with. If you click around a bit you see that within the 5 year time windows some genres become signficant, others stay signficant and some become insignificant. However, this is the most basic form of a regression and correlational at best. Therefore we are going to extent this formula a bit and see how it evolves to something that may become a litlle more causal.

## adding fixed effects
### titleType
We are observing behavior over time. But we are currently observing behavior for multiple types of behavior. Or more speicifally, for both movies AND series. But these are two different things. So while we still want to know the general genre prefference trends, we need to adjust for movie vs. series.

```{r}
fixed_type_model <- feols(averageRating ~ drama + romance + war + crime + thriller+ history + comedy + fantasy + adventure + mystery + biography + action + scifi + western + horror + sport + documentary + musical + filmnoir + animation + adult + gameshow + realitytv + talkshow + short + news | titleType,
                                data = movie_data_test,
                                split = ~ slide_window_5)

summary(fixed_type_model)
```

If you compare these results against our skeleton model you may see that the standard errors have increased. This is good! this means our analysis has become a little more robust. But let's check our r-sqaured to be sure.

```{r}

etable(simple_model)

```

```{r}
etable(fixed_type_model)

```

Good most of our r-sqaures are improving. This means this added fixed effects was a good one.

### title of movie vs. serie
Next one we want to capture some unobservable effects that are know to the raters but unknown to us. For example, script, plot and actor quality. But also things like music and other elements captured in the series that are outside of the data set.

```{r}
fixed_tt_model <- feols(averageRating ~ drama + romance + war + crime + thriller+ history + comedy + fantasy + adventure + mystery + biography + action + scifi + western + horror + sport + documentary + musical + filmnoir + animation + adult + gameshow + realitytv + talkshow + short + news | titleType,
                                data = movie_data_test,
                                split = ~ slide_window_5)

```
Last, because while out regression assumptions are mostly respected we still may want to increase the robustness of the coefficients. We do this by loosening these assumptions a little, given that hetroskedacity appears to be a little shady we loosen that assumption a little and then check the r sqaured again.

```{r assumptions}

fixed_tt_model <- feols(averageRating ~ drama + romance + war + crime + thriller+ history + comedy + fantasy + adventure + mystery + biography + action + scifi + western + horror + sport + documentary + musical + filmnoir + animation + adult + gameshow + realitytv + talkshow + short + news | titleType ,
                                vcov = "hetero",
                                data = movie_data_test,
                                split = ~ slide_window_5)

etable(fixed_tt_model)
```
Good this has a small but positive effect. Now we want to plot the results.

```{r plotting results}
?etable()
```

### 2024-03-13 SRC/Data_Prep/Data_prep.R

@@ -1,46 +1,63 @@
-#Now let's think about some operalization basics. Or more specifically, the operalization of our variables.
+install.packages("tidyverse")
+install.packages("tidyr")
+install.packages("dplyr")
+install.packages("stringr")
+library(tidyverse)
+library(tidyr)
+library(dplyr)
+library(stringr)
 
-#starting with out DV: ratings
-print(summary(movie_data$averageRating))
+#input
+movie_data <- read_csv("movie_data.csv")
 
-#Okay. So the scale is okay BUT remember that these are AVERAGE ratings, and that on average ratings 1 and 10 are quite extreem and frankly, unrealistic.
-#let's visualize how ratings are distributed
+#clean raw 
+movie_data <- movie_data %>%
+  mutate(across(c(tconst, directors, writers, titleType, isAdult,genres, parentTconst,isOriginalTitle, types, originalTitle), as.factor)) %>%
+  mutate(across(c(averageRating,numVotes,runtimeMinutes, title, seasonNumber, episodeNumber), as.numeric)) 
 
-ggplot(movie_data), aes(x = averageRating)) +
-  geom_histogram(binwidth = 1, fill = "darkorange", color = "black") +
-  labs(title = "Distribution of averageRating",
-       x = "Average Rating",y = "Frequency") +
-  scale_x_continuous(breaks = seq(0, 10, by = 1)) +  
-  theme_minimal()
+movie_data <- movie_data %>% filter(numVotes> 100) %>%
+  filter(isOriginalTitle== 1) %>%
+  distinct(primaryTitle, .keep_all = TRUE) 
 
-ggplot(movie_data, aes(x = averageRating)) +
-  geom_histogram(binwidth = 0.1, fill = "orange", color = "black") +
-  scale_x_continuous(breaks = seq(0, 10, by = 0.5), limits = c(0, 10), labels = scales::number_format(accuracy = 0.1)) +
-  labs(x = "averageRating", y = "Frequency") +
-  theme_minimal()
+movie_data<- movie_data %>% 
+  filter(titleType %in% c("movie", "tvMovie", "tvMiniSeries", "tvSeries"))
 
-#as you can see there appears to be a normal distribution that is slightly skewed to the left.
-#If you think logically about this this may be a result from the number of reviews given as opposed to the actual rating
+movie_data <- movie_data %>%
[…]

### 2024-03-15 src/data_prep/data_prep.Rmd
removed all capitals in folder names and file names

# Cleaning the Data
So after retrieving and mergig our data directly form the IMBD site, we now need to chcek and clean the data. In this markdown the data set is cleaned, reformatted and restructured.

```{r libraries, message=FALSE, warning=FALSE}
install.packages("tidyverse")
install.packages("tidyr")
install.packages("dplyr")
install.packages("stringr")

library(tidyverse)
library(tidyr)
library(dplyr)
library(stringr)
```

```{r reformatting the data, message=FALSE, warning=FALSE}
movie_data <- read_csv(movie_data)

movie_data <- movie_data %>%
  mutate(across(c(tconst, directors, writers, titleType, isAdult,genres, parentTconst,isOriginalTitle, types, originalTitle), as.factor)) %>%
  mutate(across(c(averageRating,numVotes,runtimeMinutes, title, seasonNumber, episodeNumber), as.numeric))

```

First, let's think about some operalization basics. Or more specifically, the operalization of our variables.

## starting with out DV: ratings
```{r Raw DV print}
print(summary(movie_data$averageRating))
```

Okay. So the scale is okay BUT remember that these are AVERAGE ratings, and that on average ratings 1 and 10 are quite extreem and frankly, unrealistic.

let's visualize how ratings are distributed

```{r DV plots, message=FALSE, warning=FALSE}
ggplot((movie_data), aes(x = averageRating)) +
  geom_histogram(binwidth = 1, fill = "darkorange", color = "black") +
  labs(title = "Distribution of averageRating",
       x = "Average Rating",y = "Frequency") +
  scale_x_continuous(breaks = seq(0, 10, by = 1)) +  
  theme_minimal()
```

```{r}
ggplot(movie_data, aes(x = averageRating)) +
  geom_histogram(binwidth = 0.1, fill = "orange", color = "black") +
  scale_x_continuous(breaks = seq(0, 10, by = 0.5), limits = c(0, 10), labels = scales::number_format(accuracy = 0.1)) +
  labs(x = "averageRating", y = "Frequency") +
  theme_minimal()
```
As you can see there appears to be a normal distribution that is slightly skewed to the left.
If you think logically about this this may be a result from the number of reviews given as opposed to the actual rating

```{r DV vs NumVotes, message=FALSE, warning=FALSE}
print(summary(movie_data$numVotes))
```

Do you see how the average movie only has 106 votes? Or even 5! that will defiantely influence the average

```{r Plot DV and numVotes, message=FALSE, warning=FALSE}
ggplot(movie_data, aes(x = numVotes)) +
  geom_dotplot(fill = "darkorange", color = "black", binwidth = 500) +
  labs(title = "Distribution of numVotes",
       x = "Number of Votes", y = "Frequency") + 
  theme_minimal()

movie_data$numVotes_group <- cut(movie_data$numVotes, breaks = c(-Inf, 50, Inf), labels = c("Below 50", "Above 50"))
print(table(movie_data$numVotes_group))
````

Okay, so let's filter some of there observations out. These observations are not deleted. But they are simply left behind in the corner. We want reliable data and these observation are unlikely to be reliable. But instead of arbritarily unselecting stuff we should plot the data and see where some issues lie.

```{r Filtering DV, message=FALSE, warning=FALSE}

below_100 <- movie_data %>%
  select(numVotes) %>%
  filter(numVotes < 100)

ggplot(below_100, aes(x = numVotes)) +
  geom_histogram() +
  labs(title = "Distribution of numVotes Below 100",
       x = "Group (Interval of 10)", y = "Number of Votes") +
  theme_minimal()
```

So as you may have seen these observation are heavily left skewed. So we are indeed likely to get these extreme average rating value's from the observations that have very few number of ratings.

Let's filter these observations out now.

```{r}
movie_data <- movie_data %>%
  filter(numVotes > 100) 
```

## IV data_set

Now that we have cleaned our DV. let's look at our IV's. First are some basic decisions. Movies are presented multiple times, in multiple countries. So we want to filter on the original title.
```{r}
movie_data <- movie_data %>%
  filter(isOriginalTitle== 1) %>%
  distinct(primaryTitle, .keep_all = TRUE) 
```

Next, we want to make sure we can differentiate between movie vs. series. This is because we  aren interested in generes, and those may be dependent on wether it is a movie vs. series. But we also want to see if we can solve some missing values and drop some irrelevant columns about attributes.

```{r}
movie_data<- movie_data %>% 
  filter(titleType %in% c("movie", "tvMovie", "tvMiniSeries", "tvSeries"))

movie_data <- movie_data %>%
  mutate(movie_dummy = ifelse(str_detect(titleType, regex("movie", ignore_case = TRUE)), 1, 0),
         newfilm_dummy = ifelse(startYear > 1999, 1, 0),
         above_avg = ifelse(averageRating > mean(averageRating), 1, 0),
         drama_dummy = ifelse(str_detect(genres, regex("drama", ignore_case = TRUE)), 1, 0)) %>%
  filter(drama_dummy == 1) %>%
  select(-attributes, -ordering, -region, -language, -isOriginalTitle, -parentTconst, -episodeNumber, -seasonNumber, -title, -originalTitle)

```

We are interest in genre patterns over time. However, these patterns may change not as quickly as on a yearly basis. Therefore, we construct a window that captures 5 years of viewer patterns. Because we do not know how these averRating votes we dynamic over time (for series), we assume that the yearStart is the year in which the most number of votes (numVotes) are generated. This is logical, because if this is positive the series will be continued, and if the reveiws are negative the series will be liekly to be discontinued. How the rating drops as the perc quality of the series drops over time, is for the orupose of this study left out of the equation.

```{r}
movie_data <- movie_data %>%
  select(tconst, averageRating,numVotes, titleType, startYear, runtimeMinutes, genres)

movie_data %>%
  group_by(startYear) %>%
  count()

# Assuming movie_data is your data frame
movie_data <- movie_data %>%
  filter(startYear >= 1925) %>%
  mutate(slide_window_5 = cut(startYear, breaks = seq(1925, 2025, by = 5), labels = paste(seq(1925, 2020, by = 5), "-", seq(1929, 2024, by = 5)), include.lowest = TRUE))

movie_data %>%
  group_by(slide_window_5) %>%
  count()
```

Excellent, we now have a window time frame for out analysis. Next we pivot the genres wider to that they can be nicely formatted for out analysis.

```{r}
movie_data <- movie_data %>%
  mutate(genres = tolower(genres)) %>%
  separate_rows(genres, sep = ",") %>%
  mutate(genres = as.factor(genres))
```

Good. But before we can continue we have to do some 'eye-conemetrics' and show if there might be data pattern before we run our analysis. First, we look at how number of votes and rating behave for each genre.
```{r}
ggplot(movie_data, aes(x = numVotes, y = averageRating, color= genres)) +
  geom_point() + 
  facet_wrap(~genres)
```
As you can see there is only a very small patern there. Typically, very few votes lead to all types of values, including extreme ones. However, as the number of votes seem to increase this extreme pattern decresaes slightly. This means that the number of votes continues to be relevant for our analysis and may even bias our results.

Let's see how the actual ratings are then distrubuted across genres
```{r}

ggplot(movie_data, aes(averageRating, color= genres))+
  geom_bar() +
  facet_wrap(~genres)
```

As you can see, most of the genres appear to have some normal distribution going on. This is great! let's look at it with a qq plot to confirm our enthousiasm.

```{r}
ggplot(movie_data, aes(sample = averageRating, color = genres)) +
  stat_qq() +
  facet_wrap(~genres)
```

Okay, so it looks like there is some normal distribution. How about homoskedacity?

```{r}
residuals <- movie_data$averageRating - mean(movie_data$averageRating)
fitted_values <- movie_data$averageRating

# Create a data frame for plotting
plot_data <- data.frame(Fitted_Values = fitted_values, Residuals = residuals)

# Plot residuals versus fitted values
ggplot(plot_data, aes(x = Fitted_Values, y = Residuals)) +
  geom_point() +
  geom_smooth(method = "loess", se = FALSE) +  # Add a smooth line to visualize any patterns
  labs(x = "Fitted Values", y = "Residuals") +  # Add axis labels
  ggtitle("Residuals vs. Fitted Values")  # Add a plot title
```

That also looks suspiciously good! How about independence?

```{r}

# Calculate residuals
residuals <- movie_data$averageRating - mean(movie_data$averageRating)

# Create a sequence of indices
indices <- seq_along(residuals)

# Create a data frame for plotting
plot_data <- data.frame(Index = indices, Residuals = residuals)

# Plot residuals versus index
ggplot(plot_data, aes(x = Index, y = Residuals)) +
  geom_point() +
  geom_smooth(method = "loess", se = FALSE) +  
  labs(x = "Index", y = "Residuals") +  
  ggtitle("Residuals vs. Index")
```

Linearity looks chaotics but okay. It may be a little smaller on the left and increases to the right but this is very little. So last, linearity. This is tricky, because there is no reason for genre to lead to a higher or lower rating. This is really specific to the watcher and also how the movie/series are doing. But when we add the time variable it can be that there is a relation between these elements, albeit unlikely to be linear.

```{r}
ggplot(movie_data, aes(x = slide_window_5, y = averageRating)) +
  geom_point() +
  facet_wrap(~genres)
````

Okay well that not real linear. There is some trend though. So we are going to continue with out analysis. 
However Let's clean the data set a little so each genre is a neat dummy.

```{r}
movie_data <- movie_data %>%
  mutate(genre_dummy = 1) %>%
  pivot_wider(names_from = genres, values_from = genre_dummy, values_fill = list(genre_dummy = 0)) %>%
  rename(scifi = `sci-fi`) %>%
  rename(filmnoir = `film-noir`) %>%
  rename(gameshow = `game-show`) %>%
  rename(realitytv = `reality-tv`) %>%
  rename(talkshow = `talk-show`)

```

## Let's save our data file
Don't leave before saving! 
```{r save file}
write_csv(movie_data, "movie_data_cleaned.csv")
```

### 2024-03-15 SRC/Data_Prep/Data_prep.Rmd

@@
 ```{r libraries, message=FALSE, warning=FALSE}
-install(tidyverse)
+install.packages("tidyverse")
+install.packages("tidyr")
+install.packages("dplyr")
+install.packages("stringr")
+
 library(tidyverse)
+library(tidyr)
+library(dplyr)
+library(stringr)
 ```
@@
 movie_data <- movie_data %>%
-  mutate(across(c(tconst, directors, writers, titleType, isAdult,genres, parentTconst,region,language,isOriginalTitle), as.factor)) %>%
-  mutate(across(c(averageRating,numVotes,runtimeMinutes, title,seasonNumber, episodeNumber), as.numeric)) %>%
-  mutate(across(c(primaryTitle, originalTitle,types, attributes),as.string))
+  mutate(across(c(tconst, directors, writers, titleType, isAdult,genres, parentTconst,isOriginalTitle, types, originalTitle), as.factor)) %>%
+  mutate(across(c(averageRating,numVotes,runtimeMinutes, title, seasonNumber, episodeNumber), as.numeric))
+
 ```
@@
 
-# starting with out DV: ratings
+## starting with out DV: ratings
 ```{r Raw DV print}
@@
 
-# IV data_set
+## IV data_set
 
-Now that we have clean
+Now that we have cleaned our DV. let's look at our IV's. First are some basic decisions. Movies are presented multiple times, in multiple countries. So we want to filter on the original title.
+```{r}
+movie_data <- movie_data %>%
+  filter(isOriginalTitle== 1) %>%
+  distinct(primaryTitle, .keep_all = TRUE) 
+```
+
+Next, we want to make sure we can differentiate between movie vs.
+series.
+This is because we  aren interested in generes, and those may be dependent on wether it is a movie vs.
+series.
+But we also want to see if we can solve some missing values and drop some irrelevant columns about attributes.
+
+```{r}
+movie_data<- movie_data %>% 
+  filter(titleType %in% c("movie", "tvMovie", "tvMiniSeries", "tvSeries"))
+
+movie_data <- movie_data %>%
+  mutate(movie_dummy = ifelse(str_detect(titleType, regex("movie", ignore_case = TRUE)), 1, 0),
+         newfilm_dummy = ifelse(startYear > 1999, 1, 0),
+         above_avg = ifelse(averageRating > mean(averageRating), 1, 0),
+         drama_dummy = ifelse(str_detect(genres, regex("drama", ignore_case = TRUE)), 1, 0)) %>%
+  filter(drama_dummy == 1) %>%
+  select(-attributes, -ordering, -region, -language, -isOriginalTitle, -parentTconst, -episodeNumber, -seasonNumber, -title, -originalTitle)
+
+```
+
+We are interest in genre patterns over time.
+However, these patterns may change not as quickly as on a yearly basis.
+Therefore, we construct a window that captures 5 years of viewer patterns.
+Because we do not know how these averRating votes we dynamic over time (for series), we assume that the yearStart is the year in which the most number of votes (numVotes) are generated.
+This is logical, because if this is positive the series will be continued, and if the reveiws are negative the series will be liekly to be discontinued.
+How the rating drops as the perc quality of the series drops over time, is for the orupose of this study left out of the equation.
+
+```{r}
+movie_data <- movie_data %>%
+  select(tconst, averageRating,numVotes, titleType, startYear, runtimeMinutes, genres)
+
+movie_data %>%
+  group_by(startYear) %>%
+  count()
+
+# Assuming movie_data is your data frame
+movie_data <- movie_data %>%
+  filter(startYear >= 1925) %>%
+  mutate(slide_window_5 = cut(startYear, breaks = seq(1925, 2025, by = 5), labels = paste(seq(1925, 2020, by = 5), "-", seq(1929, 2024, by = 5)), include.lowest = TRUE))
+
+movie_data %>%
+  group_by(slide_window_5) %>%
+  count()
+```
+
+Excellent, we now have a window time frame for out analysis. Next we pivot the genres wider to that they can be nicely formatted for out analysis.
+
+```{r}
+movie_data <- movie_data %>%
+  mutate(genres = tolower(genres)) %>%
+  separate_rows(genres, sep = ",") %>%
+  mutate(genres = as.factor(genres))
+```
+
+Good.
+But before we can continue we have to do some 'eye-conemetrics' and show if there might be data pattern before we run our analysis.
+First, we look at how number of votes and rating behave for each genre.
+```{r}
+ggplot(movie_data, aes(x = numVotes, y = averageRating, color= genres)) +
+  geom_point() + 
+  facet_wrap(~genres)
+```
+As you can see there is only a very small patern there.
+Typically, very few votes lead to all types of values, including extreme ones.
+However, as the number of votes seem to increase this extreme pattern decresaes slightly.
+This means that the number of votes continues to be relevant for our analysis and may even bias our results.
+
+Let's see how the actual ratings are then distrubuted across genres
+```{r}
+
+ggplot(movie_data, aes(averageRating, color= genres))+
+  geom_bar() +
+  facet_wrap(~genres)
+```
+
+As you can see, most of the genres appear to have some normal distribution going on. This is great! let's look at it with a qq plot to confirm our enthousiasm.
+
+```{r}
+ggplot(movie_data, aes(sample = averageRating, color = genres)) +
+  stat_qq() +
+  facet_wrap(~genres)
+```
+
+Okay, so it looks like there is some normal distribution. How about homoskedacity?
+
+```{r}
+residuals <- movie_data$averageRating - mean(movie_data$averageRating)
+fitted_values <- movie_data$averageRating
+
+# Create a data frame for plotting
+plot_data <- data.frame(Fitted_Values = fitted_values, Residuals = residuals)
+
+# Plot residuals versus fitted values
+ggplot(plot_data, aes(x = Fitted_Values, y = Residuals)) +
+  geom_point() +
+  geom_smooth(method = "loess", se = FALSE) +  # Add a smooth line to visualize any patterns
+  labs(x = "Fitted Values", y = "Residuals") +  # Add axis labels
+  ggtitle("Residuals vs. Fitted Values")  # Add a plot title
+```
+
+That also looks suspiciously good! How about independence?
+
+```{r}
+
+# Calculate residuals
+residuals <- movie_data$averageRating - mean(movie_data$averageRating)
+
+# Create a sequence of indices
+indices <- seq_along(residuals)
+
+# Create a data frame for plotting
+plot_data <- data.frame(Index = indices, Residuals = residuals)
+
+# Plot residuals versus index
+ggplot(plot_data, aes(x = Index, y = Residuals)) +
+  geom_point() +
+  geom_smooth(method = "loess", se = FALSE) +  
+  labs(x = "Index", y = "Residuals") +  
+  ggtitle("Residuals vs. Index")
+```
+
+Linearity looks chaotics but okay.
+It may be a little smaller on the left and increases to the right but this is very little.
+So last, linearity.
+This is tricky, because there is no reason for genre to lead to a higher or lower rating.
+This is really specific to the watcher and also how the movie/series are doing.
+But when we add the time variable it can be that there is a relation between these elements, albeit unlikely to be linear.
+
+```{r}
+ggplot(movie_data, aes(x = slide_window_5, y = averageRating)) +
+  geom_point() +
+  facet_wrap(~genres)
+````
+
+Okay well that not real linear. There is some trend though. So we are going to continue with out analysis. 
+However Let's clean the data set a little so each genre is a neat dummy.
+
+```{r}
+movie_data <- movie_data %>%
+  mutate(genre_dummy = 1) %>%
+  pivot_wider(names_from = genres, values_from = genre_dummy, values_fill = list(genre_dummy = 0)) %>%
+  rename(scifi = `sci-fi`) %>%
+  rename(filmnoir = `film-noir`) %>%
+  rename(gameshow = `game-show`) %>%
+  rename(realitytv = `reality-tv`) %>%
+  rename(talkshow = `talk-show`)
+
+```
+
+## Let's save our data file
+Don't leave before saving! 
+```{r save file}
+write_csv(movie_data, "movie_data_cleaned.csv")
+```

### 2024-03-15 SRC/analysis/regression_analysis.Rmd

@@
 mdc <- read_csv("movie_data_cleaned.csv")
-
 ```
@@
 simple_model <- feols(averageRating ~ drama + romance + war + crime + thriller+ history + comedy + fantasy + adventure + mystery + biography + action + scifi + western + horror + sport + documentary + musical + filmnoir + animation + adult + gameshow + realitytv + talkshow + short + news,
-                      data = movie_data_test,
+                      data = mdc,
                       split = ~ slide_window_5)
@@
 fixed_type_model <- feols(averageRating ~ drama + romance + war + crime + thriller+ history + comedy + fantasy + adventure + mystery + biography + action + scifi + western + horror + sport + documentary + musical + filmnoir + animation + adult + gameshow + realitytv + talkshow + short + news | titleType,
-                                data = movie_data_test,
+                                data = mdc,
                                 split = ~ slide_window_5)
@@
 fixed_tt_model <- feols(averageRating ~ drama + romance + war + crime + thriller+ history + comedy + fantasy + adventure + mystery + biography + action + scifi + western + horror + sport + documentary + musical + filmnoir + animation + adult + gameshow + realitytv + talkshow + short + news | titleType,
-                                data = movie_data_test,
+                                data = mdc,
                                 split = ~ slide_window_5)
@@
 
-fixed_tt_model <- feols(averageRating ~ drama + romance + war + crime + thriller+ history + comedy + fantasy + adventure + mystery + biography + action + scifi + western + horror + sport + documentary + musical + filmnoir + animation + adult + gameshow + realitytv + talkshow + short + news | titleType ,
+fixed_tth_model <- feols(averageRating ~ drama + romance + war + crime + thriller+ history + comedy + fantasy + adventure + mystery + biography + action + scifi + western + horror + sport + documentary + musical + filmnoir + animation + adult + gameshow + realitytv + talkshow + short + news | titleType ,
                                 vcov = "hetero",
-                                data = movie_data_test,
+                                data = mdc,
                                 split = ~ slide_window_5)
 
-etable(fixed_tt_model)
+etable(fixed_tth_model)
 ```
@@
 ```{r plotting results}
-?etable()
+
+#make a plot that suits
+
 ```

### 2024-03-15 gen/paper/paper.Rmd

---
title: "Investigating the influence of genre preferences on movie/series rating patterns over time"
author: Team 1 - Timo Philipse, Bram Teunissen, Rodrigo Pačeko Rudzājs, Dian de Ridder & Linda van den Boogaart
output:
  html_document: default
---

# Research motivation
The entertainment industry is a dynamic industry. Consumer preferences continuously change, and new movies and series are continuously being produced. Genre continues to be an important topic in the entertainment industry. Genre preferences indicate what consumers liked to watch in the past, and therefore probably also would like to watch in the future. Thus, genre can serve as a selection criteria, based on which consumers decide whether to watch a certain movie or not. Therefore, an understanding of genre preferences gives movie producers a direction on what type of genre they should adopt to increase chances of success and to best deliver the message they want to bring across. Consequently, it is important to investigate the evolution of consumers’ genre preferences over time.

## Research question
In this paper we aim to answer the following research question:

**How do consumers' movie genre preferences change over time?**

## Research method
In this paper we investigate consumers’ movie and series preferences using five datasets containing movie data. First, these datasets are merged, inspected, and cleaned Next, the data is analyzed  using regression analysis. Consumers' movie/serie ratings (averageRatings) serve as the dependent variable. Consequently, the explanatory variables are regressed on averageRatings. The explanatory variables are:

* Genre
* Series vs Movies 
* Running Time 
* Director 
* Adult title vs non-adult title
* Date

To improve the reliability of our results, a cut off based on the number of votes on the movies and series will be used. Since the dependent variable is **average** ratings, movies/series with only a few votes may receive more extreme average ratings. This can be the case because each rating, including the extreme ones, receives more weight when calculating the average, simply because there are only a few ratings. So, the average ratings may be more extreme, causing to skew the overall results. Therefore, movies/series receiving a number of votes that are below the cut off won't be included in the regression analysis.

## Results

## Discussion & conclusion

### 2024-03-15 gen/paper/paper.Rmd
worked until results section

@@
 ## Research method
-In this paper we investigate consumers’ movie and series preferences using five datasets containing movie data.
-First, these datasets are merged, inspected, and cleaned Next, the data is analyzed  using regression analysis.
-Consumers' movie/serie ratings (averageRatings) serve as the dependent variable.
-Consequently, the explanatory variables are regressed on averageRatings.
-The explanatory variables are:
+In this paper we investigate consumers’ movie and series preferences using five of IMDb's datasets containing movie data.
+First, these datasets are loaded, cleaned, inspected, merged and cleaned.
+Next, the data is analyzed using a regression analysis.
+This regression analysis regresses all movie and serie genre's against the average rating's over a period of 5 years.
+Additionally, the variables title, movieType and time are used as control variables to improve the interpret ability of the estimates.
 
-* Genre
-* Series vs Movies 
-* Running Time 
-* Director 
-* Adult title vs non-adult title
-* Date
+```{r message=FALSE, warning=FALSE}
+my_data <- data.frame(
+  Name = c("Average Rating", "Genre Types", "titleType", "Title", "5 Year Window"),
+  Contents = c("The average rating on IMBd per title of a given movie or series", "Genre Types is cluster for all 26 genre dummies that contain the value 1 if the movie or serie contains that genre and otherwise 0", "This variable indicated whether a title is a movie or a series", "the title is the given title of any unique movie or series", "The 5 year windown (or ' slide_window_5' indicates between what 5 year windown a movie or series belongs to.
+For example a movie from 2003 belong to 2000-2004")
+)
 
-To improve the reliability of our results, a cut off based on the number of votes on the movies and series will be used.
-Since the dependent variable is **average** ratings, movies/series with only a few votes may receive more extreme average ratings.
+my_table <- kable(my_data, format = "html", escape = FALSE) %>%
+  kable_styling(full_width = FALSE) %>%
+  row_spec(0, bold = TRUE) %>%
+  column_spec(1, width = "15%")  # Adjust the width of the first column as needed
+
+# Print the table
+print(my_table)
+```
+
+### Average Movie Rating
+The average IMBd rating is used as the outcome variable for the analysis.
+However this average rating is influenced by the number of votes that compile this average.
 This can be the case because each rating, including the extreme ones, receives more weight when calculating the average, simply because there are only a few ratings.
 So, the average ratings may be more extreme, causing to skew the overall results.
-Therefore, movies/series receiving a number of votes that are below the cut off won't be included in the regression analysis.
+Therefore, movies/series receiving a number of votes that are below the cut off of a hundred will not be included in the regression analysis.
+
+### Genres
+Genres are used as the explanatory variable in the analysis.
+However, because they are nested within the original data set the are first un-nested and then pivoted wider.
+As a result a data with 27 dummies was constructed that could assessed separately in the analysis.
+
+### Fixed Effects
+Given that the measurement of genre preferences over time is a construct that is viable to many unobserables, fixed effects were added to partially capture these unobservant.
+More specifically the type of title (movie vs.
+series) and title were added.
+To give an example, it could be that for movies, people prefer something with a little more drama that they would for a series or vice-versa.
+
+A point of concern however, is that these average ratings are not measured over time but are a fixed sum up to and including the data of analysis.
+This means that if series fall out of favor and their rating drops this remains unobservant.
+Given that the continuation of series is determined by their success (a second season is not produced if the first one was a flop) the following assumption can be made: if a genre is not preffered throughout the continuance of a series, the rating is low in the starting year and thus unlikely to be significant.
+
+### capturing prefferences over time
+Last to actually see how preferences change over time we build on the assumption that if a movie or series is a success they gain many positive rating in the beginning and less so over time.
+As a result there is a peak during (first season) release, and allows us to only use the startYear as a means to calculate behavior over time.
+Yet, the individual year are unlikely to have a remarkable effect on the genre prefference trends This is because the effects are so nuanced that they are unlikely to be detected.
+Therefore, to solve this a five year window was created that captures all genre prefferences for that period of time
+
+### assumption
+All assumption associated with regression were checked via a visual inspection. Only linearity appeared to be satisfied.
+
+```{r Normality, echo=FALSE, warning=FALSE}
+movie_data <- read_csv(movie_data_cleaned)
+ggplot(movie_data, aes(x = slide_window_5, y = averageRating, fill=genres)) +
+  geom_point() +
+  facet_wrap(~genres)
+
+```
+While homoskedacity and independence appeared to be moderate at best.
+
+```{r Independence, echo=FALSE}
+# Calculate residuals
+residuals <- movie_data$averageRating - mean(movie_data$averageRating)
+
+# Create a sequence of indices
+indices <- seq_along(residuals)
+
+# Create a data frame for plotting
+plot_data <- data.frame(Index = indices, Residuals = residuals)
+
+# Plot residuals versus index
+ggplot(plot_data, aes(x = Index, y = Residuals, fill= "green")) +
+  geom_point() +
+  geom_smooth(method = "loess", se = FALSE) +  
+  labs(x = "Index", y = "Residuals") +  
+  ggtitle("Residuals vs. Index")
+```
+
+```{r Homosk, echo=FALSE}
+residuals <- movie_data$averageRating - mean(movie_data$averageRating)
+fitted_values <- movie_data$averageRating
+
+# Create a data frame for plotting
+plot_data <- data.frame(Fitted_Values = fitted_values, Residuals = residuals)
+
+# Plot residuals versus fitted values
+ggplot(plot_data, aes(x = Fitted_Values, y = Residuals)) +
+  geom_point() +
+  geom_smooth(method = "loess", se = FALSE) +  # Add a smooth line to visualize any patterns
+  labs(x = "Fitted Values", y = "Residuals") +  # Add axis labels
+  ggtitle("Residuals vs. Fitted Values")  # Add a plot title
+```
+
+Linearity appared to be violated the most with a widening trend for all genres as the years evolved.
+
+```{r linearity, echo=FALSE}
+ggplot(movie_data, aes(x = slide_window_5, y = averageRating, fill=genres)) +
+  geom_point() +
+  facet_wrap(~genres)
+````
+
+Regardless of these results the decision was made to continue with the analysis.
+This is because the r package fixest allows for modification in the mixed model analysis that help overcome these limitations.
+For example, the package allows for clustering of different groups of residuals.
+While this does not entirely mitigate the assumption concerns it does help with them.
 
@@
 
-## Discussion & conclusion
+## Discussion
+The results of this analysis can be interpreted as correlation given the vast amount of assumptions.
+While this has been partially mitigated by loosening some of the underlying assumptions the fact remains that these appears trend observations.
+
+Ths research can be extended in 3 distinct ways.
+
+First, researchers may want to make use of dynamic review data that is not an accumulation of a point in time.
+Currently the sole measure of the average reviews resulted in two major assumptions in the analysis.
+The first assumption refers to series and franchise continuation.
+E.g., if the first film or series was not successful there is no follow up.
+And the second assumption refers to fact that the year window is based on the startYear of the movie and series.
+By looking at dynamic data researchers can also observe if genres fall out of favor in specific conditions.
+For example, as the series continue do people tire of the interpretation of the genre or is the genre in general less popular?
+
+Second, researchers may benefit by including data from multiple sources.
+Currently the analysis is limited to IMBd data but there are also other sources such as rottentomato's for example.
+By combining these data sets the interpretation of the results become less bias by the data platform.
+For example, it may be that people of higher age groups typically review on IMBd and younger groups adopted commentator's.
+By broadening the data sources the generalization of the results increase.
+
+Last, researchers may benefit by including additional control variables such as gdp and reported population happiness scales.
+Given that the movie and series market is an indulgent market it may be that genres did not fall out of favor but that people could not afford to watch movies and series.
+Or it may be that there were other matters stirring in the population which made them more happy or sad.
+These factors influence consumption patterns and thus ratings.
+By broadening the scope of the analysis result become more reliable.
+
+# Conclusion
+This research illustrates that consumer reported genre preferences appear to change over time.
+Yet, further research is required to analyse the exact depth of these preferences and their generalizability.
+
+Overall, the genres crime, action, and animation appear to be favored across time.
+Additionally, the genre comedy fell in favor while the genre aventure and sci-fi appeared to experience peak year during .
+In constract the genres x y and z fell out of favor.
+
+git mv old_file.txt new_file.txt
+git commit -m "Rename file from old_file.txt to new_file.txt"

### 2024-03-15 gen/paper/paper.Rmd
Took out some spelling mistakes, added (installing &) loading required packages (but needs to be updated on automation later on), added some comments in R code chuncks to work on later on (importing previous plot outputs instead of data file)

@@
 In this paper we investigate consumers’ movie and series preferences using five of IMDb's datasets containing movie data.
-First, these datasets are loaded, cleaned, inspected, merged and cleaned.
+First, these datasets are loaded, inspected, merged and cleaned.
 Next, the data is analyzed using a regression analysis.
-This regression analysis regresses all movie and serie genre's against the average rating's over a period of 5 years.
-Additionally, the variables title, movieType and time are used as control variables to improve the interpret ability of the estimates.
+This regression analysis regresses all movie and series genres against the average ratings over a period of 5 years.
+Additionally, the variables title, movieType and time are used as control variables to improve the interpretability of the estimates.
 
@@
 )
+
+# Also still need to update/automate installing packages.Will look into that as well later on. 
+#install.packages("tidyverse")
+#install.packages("knitr")
+#install.packages("kableExtra")
+
+library(tidyverse)
+library(knitr)
+library(kableExtra)
 
@@
 However, because they are nested within the original data set the are first un-nested and then pivoted wider.
-As a result a data with 27 dummies was constructed that could assessed separately in the analysis.
+As a result a dataset with 27 dummies was constructed that could assessed separately in the analysis.
 
 ### Fixed Effects
-Given that the measurement of genre preferences over time is a construct that is viable to many unobserables, fixed effects were added to partially capture these unobservant.
+Given that the measurement of genre preferences over time is a construct that is viable to many unobservables, fixed effects were added to the regression analysis to partially capture these unobservables.
 More specifically the type of title (movie vs.
 series) and title were added.
-To give an example, it could be that for movies, people prefer something with a little more drama that they would for a series or vice-versa.
+To give an example, it could be that for movies people prefer something with a little more drama that they would for a series or vice-versa.
 
-A point of concern however, is that these average ratings are not measured over time but are a fixed sum up to and including the data of analysis.
+A point of concern, however, is that these average ratings are not measured over time but are a fixed sum up to and including the data of analysis.
 This means that if series fall out of favor and their rating drops this remains unobservant.
-Given that the continuation of series is determined by their success (a second season is not produced if the first one was a flop) the following assumption can be made: if a genre is not preffered throughout the continuance of a series, the rating is low in the starting year and thus unlikely to be significant.
+Given that the continuation of series is determined by their success (a second season is not produced if the first one was not successful) the following assumption can be made: if a genre is not preferred throughout the continuance of a series, the rating is low in the starting year and thus unlikely to be significant.
 
 ### capturing prefferences over time
-Last to actually see how preferences change over time we build on the assumption that if a movie or series is a success they gain many positive rating in the beginning and less so over time.
+Lastly, to actually see how preferences change over time we build on the assumption that if a movie or series is a success they gain many positive rating in the beginning and less so over time.
 As a result there is a peak during (first season) release, and allows us to only use the startYear as a means to calculate behavior over time.
-Yet, the individual year are unlikely to have a remarkable effect on the genre prefference trends This is because the effects are so nuanced that they are unlikely to be detected.
-Therefore, to solve this a five year window was created that captures all genre prefferences for that period of time
+Yet, the individual years are unlikely to have a remarkable effect on the genre preference trends This is because the effects are so nuanced that they are unlikely to be detected.
+Therefore, a five year window was created that captures all genre preferences for that period of time.
 
@@
   facet_wrap(~genres)
+# Can't we save the plot as output file in the regression.Rmd.
+In this way we don't have to load in all the data when generating this report.
+Will look into this, this note serves as a reminder for that.
+```
 
-```
-While homoskedacity and independence appeared to be moderate at best.
+Homoscedasticity and independence appeared to be moderate at best.
 
@@
   ggtitle("Residuals vs. Index")
+
+# Same as above # Can't we save the plot as output file in the regression.Rmd.
+In this way we don't have to load in all the data when generating this report.
+Will look into this, this note serves as a reminder for that.
 ```
@@
 ```{r Homosk, echo=FALSE}
+# Same as above # Can't we save the plot as output file in the regression.Rmd.
+In this way we don't have to load in all the data when generating this report.
+Will look into this, this note serves as a reminder for that.
+
 residuals <- movie_data$averageRating - mean(movie_data$averageRating)
@@
 
-Linearity appared to be violated the most with a widening trend for all genres as the years evolved.
+Linearity appeared to be violated the most with a widening trend for all genres as the years evolved.
 
 ```{r linearity, echo=FALSE}
+# Same as above # Can't we save the plot as output file in the regression.Rmd.
+In this way we don't have to load in all the data when generating this report.
+Will look into this, this note serves as a reminder for that.
 ggplot(movie_data, aes(x = slide_window_5, y = averageRating, fill=genres)) +
@@
 Regardless of these results the decision was made to continue with the analysis.
-This is because the r package fixest allows for modification in the mixed model analysis that help overcome these limitations.
+This is because the R package `fixest` allows for modification in the mixed model analysis that help overcome these limitations.
 For example, the package allows for clustering of different groups of residuals.
@@
 
-Ths research can be extended in 3 distinct ways.
+This research can be extended in 3 distinct ways.
 
@@
 E.g., if the first film or series was not successful there is no follow up.
-And the second assumption refers to fact that the year window is based on the startYear of the movie and series.
+And the second assumption refers to fact that the year window is based on the start year of the movie and series.
 By looking at dynamic data researchers can also observe if genres fall out of favor in specific conditions.
@@
 Second, researchers may benefit by including data from multiple sources.
-Currently the analysis is limited to IMBd data but there are also other sources such as rottentomato's for example.
-By combining these data sets the interpretation of the results become less bias by the data platform.
-For example, it may be that people of higher age groups typically review on IMBd and younger groups adopted commentator's.
+Currently the analysis is limited to IMBd data but there are also other sources such as Rotten Tomatos for example.
+By combining these data sets the interpretation of the results become less biased by the data platform.
+For example, it may be that people of higher age groups typically review on IMBd and younger groups adopted commentators.
 By broadening the data sources the generalization of the results increase.
 
-Last, researchers may benefit by including additional control variables such as gdp and reported population happiness scales.
+Last, researchers may benefit by including additional control variables such as GDP and reported population happiness scales.
 Given that the movie and series market is an indulgent market it may be that genres did not fall out of favor but that people could not afford to watch movies and series.
@@
 Overall, the genres crime, action, and animation appear to be favored across time.
-Additionally, the genre comedy fell in favor while the genre aventure and sci-fi appeared to experience peak year during .
+Additionally, the genres comedy fell in favor while the genres adventure and sci-fi appeared to experience peak year during XXXX.
 In constract the genres x y and z fell out of favor.
-
-git mv old_file.txt new_file.txt
-git commit -m "Rename file from old_file.txt to new_file.txt"

### 2024-03-16 src/data_prep/getting_the_data.R
fixed data saving and some efficiency issues

@@ -7,7 +7,6 @@ Data_Source <- list(
   "https://datasets.imdbws.com/title.ratings.tsv.gz",
   "https://datasets.imdbws.com/title.episode.tsv.gz",
   "https://datasets.imdbws.com/title.akas.tsv.gz",
-  "https://datasets.imdbws.com/title.crew.tsv.gz",
   "https://datasets.imdbws.com/title.basics.tsv.gz"
 )
 
@@ -18,7 +17,6 @@ for (url in Data_Source) {
         assign(file_name, read_tsv(file_name)) # Read the downloaded file into R
         file.remove(file_name) # Remove the downloaded file
 }
-
 
 #let's merge some datasets! 
 #Please take a close look at all the data sets. Do you see how they all have a label 'tconst"? that is awesome because it allows us to merge the data sets.
@@ -36,11 +34,11 @@ episodes <- episodes %>%
 #Data_set <- left_join(ratings, basics, by = "tconst")
 #while this was nice, we need a larger scale operalization.
 
-data_sets <- list(ratings, crew, basics, episode, akas)
+data_sets <- list(ratings, basics, episode, akas)
 join_column <- "tconst"
 movie_data <- Reduce(function(x, y) left_join(x, y, by = join_column), data_sets)
 
 #Awesome! Now we have running code that builds an entire dataframe from seperate ones.
 
 #now let's store the data
-write_csv(movie_data, "movie_data.csv")
+write_csv(movie_data, "src/data_prep/movie_data.csv")

### 2024-03-18 gen/paper/paper.Rmd
wrote the results section

--- 2024-03-15 gen/paper/paper.Rmd
@@
 ## Results
+The results indicated that there are different genre preferences over time.
+Out of all twenty five genres, only aighteen appeared to significantly influence the average ratings on IMBd.
+These genres were animation, biography, film-noir, fanatsy, documentary, crime, comedy, game-show, history, horror, musical, shorts, sci-fi, romance, reality-tv, news, and war.
+
+The genre history fell in favor in around the year 1960 and continued to significantly (p~1960<.01) influence the average rating until this day.
 
@@
 In constract the genres x y and z fell out of favor.
-
-git mv old_file.txt new_file.txt
-git commit -m "Rename file from old_file.txt to new_file.txt"

### 2024-03-18 gen/paper/paper.Rmd
filtered out spelling mistakes and fixed table

--- 2024-03-15 gen/paper/paper.Rmd
@@
 ---
-title: "Investigating the influence of genre preferences on movie/series rating patterns over time"
-author: Team 1 - Timo Philipse, Bram Teunissen, Rodrigo Pačeko Rudzājs, Dian de Ridder & Linda van den Boogaart
+title: Investigating the influence of genre preferences on movie/series rating patterns
+  over time
+author: "Team 1 - Timo Philipse, Bram Teunissen, Rodrigo Pačeko Rudzājs, Dian de Ridder
+  & Linda van den Boogaart"
 output:
+  pdf_document: default
   html_document: default
+editor_options:
+  markdown:
+    wrap: 72
 ---
@@
 # Research motivation
-The entertainment industry is a dynamic industry.
-Consumer preferences continuously change, and new movies and series are continuously being produced.
-Genre continues to be an important topic in the entertainment industry.
-Genre preferences indicate what consumers liked to watch in the past, and therefore probably also would like to watch in the future.
-Thus, genre can serve as a selection criteria, based on which consumers decide whether to watch a certain movie or not.
-Therefore, an understanding of genre preferences gives movie producers a direction on what type of genre they should adopt to increase chances of success and to best deliver the message they want to bring across.
-Consequently, it is important to investigate the evolution of consumers’ genre preferences over time.
+
+The entertainment industry is a dynamic industry. Consumer preferences
+continuously change, and new movies and series are continuously being
+produced. Genre continues to be an important topic in the entertainment
+industry. Genre preferences indicate what consumers liked to watch in
+the past, and therefore probably also would like to watch in the future.
+Thus, genre can serve as a selection criteria, based on which consumers
+decide whether to watch a certain movie or not. Therefore, an
+understanding of genre preferences gives movie producers a direction on
+what type of genre they should adopt to increase chances of success and
+to best deliver the message they want to bring across. Consequently, it
+is important to investigate the evolution of consumers’ genre
+preferences over time.
 
 ## Research question
+
 In this paper we aim to answer the following research question:
@@
 ## Research method
-In this paper we investigate consumers’ movie and series preferences using five of IMDb's datasets containing movie data.
-First, these datasets are loaded, cleaned, inspected, merged and cleaned.
-Next, the data is analyzed using a regression analysis.
-This regression analysis regresses all movie and serie genre's against the average rating's over a period of 5 years.
-Additionally, the variables title, movieType and time are used as control variables to improve the interpret ability of the estimates.
 
-```{r message=FALSE, warning=FALSE}
-my_data <- data.frame(
-  Name = c("Average Rating", "Genre Types", "titleType", "Title", "5 Year Window"),
-  Contents = c("The average rating on IMBd per title of a given movie or series", "Genre Types is cluster for all 26 genre dummies that contain the value 1 if the movie or serie contains that genre and otherwise 0", "This variable indicated whether a title is a movie or a series", "the title is the given title of any unique movie or series", "The 5 year windown (or ' slide_window_5' indicates between what 5 year windown a movie or series belongs to.
-For example a movie from 2003 belong to 2000-2004")
-)
+In this paper we investigate consumers’ movie and series preferences
+using five of IMDb's datasets containing movie data. First, these
+datasets are loaded, cleaned, inspected, merged and cleaned. Next, the
+data is analyzed using a regression analysis. This regression analysis
+regresses all movie and serie genre's against the average rating's over
+a period of 5 years. Additionally, the variables title, movieType and
+time are used as control variables to improve the interpret ability of
+the estimates.
 
-my_table <- kable(my_data, format = "html", escape = FALSE) %>%
-  kable_styling(full_width = FALSE) %>%
-  row_spec(0, bold = TRUE) %>%
-  column_spec(1, width = "15%")  # Adjust the width of the first column as needed
+| Name of Variable | Contents of Variable                                                                                                                                             | Used as ..
+in Analysis |
+|------------------|------------------------------------------------------------------------------------------------------------------------------------------------------------------|------------------------|
+| Average Rating   | The average rating on IMBd per title of a given movie or series.
+| Dependent Variable     |
+| Genre Types      | Genre Types is a cluster for all 26 genre dummies that contain the value 1 if the movie or series contains that genre and otherwise 0.
+| Independent Variable   |
+| titleType        | This variable indicates whether a title is a movie or a series.
+| Fixed Effect           |
+| Title            | The title is the given title of any unique movie or series                                                                                                       | Fixed Effect           |
+| 5 Year Window    | The 5 year windown (or ' slide_window_5' indicates between what 5 year window a movie or series belongs to.
+For example a movie from 2003 belonging to 2000-2004 | Split Varible          |
 
-# Print the table
-print(my_table)
+### Average Movie Rating
+
+The average IMBd rating is used as the outcome variable for the
+analysis. However, this average rating is influenced by the number of
+votes that compile this average. This can be the case because each
+rating, including the extreme ones, receives more weight when
+calculating the average, simply because there are only a few ratings.
+So, the average ratings may be more extreme, causing to skew the overall
+results. Therefore, movies/series receiving a number of votes below the
+cut-off of a hundred will not be included in the regression analysis.
+
+### Genres
+
+Genres are used as the explanatory variable in the analysis. However,
+because they are nested within the original data set they are first
+un-nested and then pivoted wider. As a result data with 27 dummies was
+constructed that could assessed separately in the analysis.
+
+### Fixed Effects
+
+Given that the measurement of genre preferences over time is a construct
+that is viable to many unobservables, fixed effects were added to
+partially capture these unobservant. More specifically the type of title
+(movie vs. series) and title were added. To give an example, it could be
+that for movies, people prefer something with a little more drama than
+they would for a series or vice-versa.
+
+A point of concern, however, is that these average ratings are not
+measured over time but are a fixed sum up to and including the data of
+analysis. This means that if series fall out of favor and their rating
+drops this remains unobservant. Given that the continuation of a series
+is determined by its success (a second season is not produced if the
+first one was a flop) the following assumption can be made: if a genre
+is not preferred throughout the continuance of a series, the rating is
+low in the starting year and thus unlikely to be significant.
+Additionally, since IMDb was not around in 1925, average ratings for
+movies and series originating from that time may be strongly biased
+because a nice selection of the population may be watching these movies
+in the first place.
+
+### Capturing preferences over time
+
+Last to see how preferences change over time we build on the assumption
+that if a movie or series is a success they gain many positive ratings
+in the beginning and less so over time. As a result, there is a peak
+during (the first season) release allowing us to only use the startYear
+as a means to calculate behavior over time. Yet, the individual years
+are unlikely to have a remarkable effect on the genre preference trends
+This is because the effects are so nuanced that they are unlikely to be
+detected. Therefore, to solve this a five-year window was created that
+captures all genre preferences for that period
+
+### Assumption
+
+All assumptions associated with regression were checked via a visual
+inspection. Only linearity appeared to be satisfied.
+
+```{r Normality, echo=FALSE, warning=FALSE}
+#insert pdf
+
 ```
 
-### Average Movie Rating
-The average IMBd rating is used as the outcome variable for the analysis.
-However this average rating is influenced by the number of votes that compile this average.
-This can be the case because each rating, including the extreme ones, receives more weight when calculating the average, simply because there are only a few ratings.
-So, the average ratings may be more extreme, causing to skew the overall results.
-Therefore, movies/series receiving a number of votes that are below the cut off of a hundred will not be included in the regression analysis.
-
-### Genres
-Genres are used as the explanatory variable in the analysis.
-However, because they are nested within the original data set the are first un-nested and then pivoted wider.
-As a result a data with 27 dummies was constructed that could assessed separately in the analysis.
-
-### Fixed Effects
-Given that the measurement of genre preferences over time is a construct that is viable to many unobserables, fixed effects were added to partially capture these unobservant.
-More specifically the type of title (movie vs.
-series) and title were added.
-To give an example, it could be that for movies, people prefer something with a little more drama that they would for a series or vice-versa.
-
-A point of concern however, is that these average ratings are not measured over time but are a fixed sum up to and including the data of analysis.
-This means that if series fall out of favor and their rating drops this remains unobservant.
-Given that the continuation of series is determined by their success (a second season is not produced if the first one was a flop) the following assumption can be made: if a genre is not preffered throughout the continuance of a series, the rating is low in the starting year and thus unlikely to be significant.
-
-### capturing prefferences over time
-Last to actually see how preferences change over time we build on the assumption that if a movie or series is a success they gain many positive rating in the beginning and less so over time.
-As a result there is a peak during (first season) release, and allows us to only use the startYear as a means to calculate behavior over time.
-Yet, the individual year are unlikely to have a remarkable effect on the genre prefference trends This is because the effects are so nuanced that they are unlikely to be detected.
-Therefore, to solve this a five year window was created that captures all genre prefferences for that period of time
-
-### assumption
-All assumption associated with regression were checked via a visual inspection. Only linearity appeared to be satisfied.
-
-```{r Normality, echo=FALSE, warning=FALSE}
-movie_data <- read_csv(movie_data_cleaned)
-ggplot(movie_data, aes(x = slide_window_5, y = averageRating, fill=genres)) +
-  geom_point() +
-  facet_wrap(~genres)
-
-```
 While homoskedacity and independence appeared to be moderate at best.
 
-```{r Independence, echo=FALSE}
-# Calculate residuals
-residuals <- movie_data$averageRating - mean(movie_data$averageRating)
-
-# Create a sequence of indices
-indices <- seq_along(residuals)
-
-# Create a data frame for plotting
-plot_data <- data.frame(Index = indices, Residuals = residuals)
-
-# Plot residuals versus index
-ggplot(plot_data, aes(x = Index, y = Residuals, fill= "green")) +
-  geom_point() +
-  geom_smooth(method = "loess", se = FALSE) +  
-  labs(x = "Index", y = "Residuals") +  
-  ggtitle("Residuals vs. Index")
+```{r}
+#insert pdf
 ```
 
-```{r Homosk, echo=FALSE}
-residuals <- movie_data$averageRating - mean(movie_data$averageRating)
-fitted_values <- movie_data$averageRating
+Linearity appeared to be violated the most with a widening trend for all
+genres as the years evolved.
 
-# Create a data frame for plotting
-plot_data <- data.frame(Fitted_Values = fitted_values, Residuals = residuals)
-
-# Plot residuals versus fitted values
-ggplot(plot_data, aes(x = Fitted_Values, y = Residuals)) +
-  geom_point() +
-  geom_smooth(method = "loess", se = FALSE) +  # Add a smooth line to visualize any patterns
-  labs(x = "Fitted Values", y = "Residuals") +  # Add axis labels
-  ggtitle("Residuals vs. Fitted Values")  # Add a plot title
+```{r}
+#insert pdf
 ```
 
-Linearity appared to be violated the most with a widening trend for all genres as the years evolved.
+Regardless of these results the decision was made to continue with the
+analysis. This is because the r package fixest allows for modification
+in the mixed model analysis that helps overcome these limitations. For
+example, the package allows for clustering of different groups of
+residuals. While this does not entirely mitigate the assumption concerns
+it does help with them.
 
-```{r linearity, echo=FALSE}
-ggplot(movie_data, aes(x = slide_window_5, y = averageRating, fill=genres)) +
-  geom_point() +
-  facet_wrap(~genres)
-````
+## Results and Discussion
+```{r}
+#insert pdf of results graph with colored dots
+```
 
-Regardless of these results the decision was made to continue with the analysis.
-This is because the r package fixest allows for modification in the mixed model analysis that help overcome these limitations.
-For example, the package allows for clustering of different groups of residuals.
-While this does not entirely mitigate the assumption concerns it does help with them.
+The results indicated that there are different genre preferences over
+time. Out of all twenty-five genres, only eighteen appeared to
+significantly influence the average ratings on IMBd. These genres were
+animation, biography, film-noir, fantasy, documentary, crime, comedy,
+game-show, history, horror, musical, shorts, sci-fi, romance,
+reality-tv, news, and war.
 
-## Results
+The genre history fell in favor in around the year 1960 and continued to
+significantly (p~1960-1964~\<.01) relate to the average rating until
+this day (p~2020-2024~ \<.001). While the genre film-noir stoped to
+significantly relate to the average ratings around the year 1950
+(p~1950-1954~=.06 , p~1955-1959~ =.49). The genres crime (p~2000-2004~
+\<.01,p~2005-2009~ \<.01), romance (p~1940-1944~ =.03, p~1945-1949~
+\<.01), horror(p~1925-1929~ =.04), game-show(p~2000-2004~ \<.01),
+reality-tv(p~1970-1974~ \<.01), sci-fi(p~1935-1939~ \<.01), and
+shorts(p~1995-1999~ \<.01, p~2005-2009~ \<.01) had a single period
+bursts were they significantly related to the average ratings. Last, the
+genres animation (p\~1940-1944 \<.01, p~1950-1954~ \<.01, p~1975-1979~
+\<.01 -up until 2024), biography (p~1935-1939~ \<.01, p~1985-1989~ \<.01
+-Up until 2024), comedy(p~1930-1934~ =.02, p~1950-1954~ =.04,
+p~1990-1994~ =.01), documentary (p~1930-1934~ \<.01, p\~1945-1949 \<.01,
+p\~1980-1984 \<.01 - up to and including p\~2015-2019 \<.01), fantasy
+(p~1930-1934~ \<.01, p~1935-1939~ \<.01, p~1945-1949~ \<.01,
+p~1970-1974~ =.03), musical(p~1960-1964~ =.09, p~1985-1989~ =.03,
+p~1990-1994~ =.02, p~2020-2024~\<.01), and war(p~1930-1934~ =.02,
+p~1945-1949~ \<.01, p~1960-1964~ =.04 up to and including p~1970-1974~
+\<.01, p~1985-1989~ \<.01 up to and including p~2005-2009~ \<.01)
+significantly were related to the average rating in burst with unrelated
+periods in between
 
-## Discussion
-The results of this analysis can be interpreted as correlation given the vast amount of assumptions.
-While this has been partially mitigated by loosening some of the underlying assumptions the fact remains that these appears trend observations.
+A reason why genres such as animation, biography, and history are so
+often correlated with the average rating over time is because these
+genres hold very unique elements. For example, take romance. In romance,
+the plays and sequence of events are often set and fail to vary. A
+watcher often knows what is going to happen next and what it may look
+like. Controversially, the genres of animation, biography, and history
+contain more unique and unpredictable elements. For example, not every
+animated movie is Frozen or the Incredibles, the history of Egypt is not
+the same as that of Amelia Earhart or even Germany, and the story of
+Elton John is different from that of Justin Timberlake.
 
-Ths research can be extended in 3 distinct ways.
+For genres like war and film-noir the correlation could be a sign of the
+times, and strongly guided by biases in the rating population. For
+example, when the genre war was indicated to be significantly related to
+average ratings it was the time the Second World War and the Cold War
+were in full motion. Therefore people who have an interest in this topic
+may like to watch propaganda movies from that time. As a result, the
+average ratings are higher because a nice of interested people is
+watching. Similar to film-noir, people who are interested in this type
+of movie or series are watching these and rating them. Therefore, there
+may be a strong instance of viewer bias present.
 
-First, researchers may want to make use of dynamic review data that is not an accumulation of a point in time.
-Currently the sole measure of the average reviews resulted in two major assumptions in the analysis.
-The first assumption refers to series and franchise continuation.
-E.g., if the first film or series was not successful there is no follow up.
-And the second assumption refers to fact that the year window is based on the startYear of the movie and series.
-By looking at dynamic data researchers can also observe if genres fall out of favor in specific conditions.
-For example, as the series continue do people tire of the interpretation of the genre or is the genre in general less popular?
+On the contrary, the genres action, adult, adventure, mystery, sport,
+thriller, and western are all insignificant and do not appear to be
+correlated to the average ratings on IMBd. A reason for this may be that
+these elements have become expected or core components of movies and
+series and therefore do not stand out. As a result, they may not
+correlate with the average rating as much as elements of a biography may
+do. It is not every day a movie or series is released that is based on
+true events.
+
+# Conclusion
+
+This research illustrates that genre preferences may be related to the
+average IMBd ratings and vary over time. While further research is
+necessary to fine-tune these claims the current research does provide
+insight into how raters' watch patterns appear to alter. For example, it
+shows that the common ingredients like romance and action may not stand
+out as much as biography and history might. Additionally, the results
+showed that The results of this analysis can be, at best, interpreted as
+correlational given the vast amount of assumptions and potential hidden
+dangers of sampling biases (e.g., film-noir and war genres). While this
+has been partially mitigated by loosening some of the underlying
+assumptions and adding fixed effects, the fact remains that these appear
+as trend observations. Therefore, the results do not necessarily
+conclude that some genres lead to higher average ratings. However, the
+results do indicate that there may be preferences over time that may
+lead to higher average ratings.
+
+## Extensions
+
+Yet, the investigation into these genres is only a starting point. Much
+more can be learned and investigated. Here are three ways in which the
+current research into how genres relate to average IMBd rating may be
+extended:
+
+First, researchers may want to make use of dynamic review data that is
+not an accumulation of a point in time. Currently, the sole measure of
+the average reviews resulted in two major assumptions in the analysis.
+The first assumption refers to series and franchise continuation. E.g.,
+if the first film or series was not successful there is no follow-up.
+And the second assumption refers to the fact that the year window is
+based on the startYear of the movie and series. By looking at dynamic
+data researchers can also observe if genres fall out of favor in
+specific conditions. For example, as the series continues do people tire
+of the interpretation of the genre, or is the genre in general less
+popular?
 
 Second, researchers may benefit by including data from multiple sources.
-Currently the analysis is limited to IMBd data but there are also other sources such as rottentomato's for example.
-By combining these data sets the interpretation of the results become less bias by the data platform.
-For example, it may be that people of higher age groups typically review on IMBd and younger groups adopted commentator's.
-By broadening the data sources the generalization of the results increase.
+Currently, the analysis is limited to IMBd data but there are also other
+sources such as rottentomato's for example. By combining these data sets
+the interpretation of the results becomes less biased by the data
+platform. For example, it may be that people of higher age groups
+typically review IMBd, and younger groups adopt commentators. By
+broadening the data sources the generalization of the results increases.
 
-Last, researchers may benefit by including additional control variables such as gdp and reported population happiness scales.
-Given that the movie and series market is an indulgent market it may be that genres did not fall out of favor but that people could not afford to watch movies and series.
-Or it may be that there were other matters stirring in the population which made them more happy or sad.
-These factors influence consumption patterns and thus ratings.
-By broadening the scope of the analysis result become more reliable.
-
-# Conclusion
-This research illustrates that consumer reported genre preferences appear to change over time.
-Yet, further research is required to analyse the exact depth of these preferences and their generalizability.
-
-Overall, the genres crime, action, and animation appear to be favored across time.
-Additionally, the genre comedy fell in favor while the genre aventure and sci-fi appeared to experience peak year during .
-In constract the genres x y and z fell out of favor.
-
-git mv old_file.txt new_file.txt
-git commit -m "Rename file from old_file.txt to new_file.txt"
+Last, researchers may benefit by including additional control variables
+such as GDP and reported population happiness scales. Given that the
+movie and series market is an indulgent market it may be that genres did
+not fall out of favor but that people could not afford to watch movies
+and series. Or it may be that other matters were stirring in the
+population which made them more happy or sad. These factors influence
+consumption patterns and thus ratings. By broadening the scope of the
+analysis results become more reliable.

### 2024-03-19 installing_packages.R
made the script to automatically install all the not yet installed packages needed for our project

@@ -1,0 +1,60 @@
+# This Rscript searches all the project's source code for references to packages,
+# and subsequently installs all packages which are needed, but yet uninstalled.
+
+# Find all source code files
+files <- list.files(
+  path = "./src", # Tells the function to only search through files in the source code folder (src)
+  pattern = '[.](R|rmd)$', # Tells the function to only list .R and .Rmd files.
+  all.files = T, # Includes invisible files as well
+  recursive = T, # Makes sure the names of the sub directories are returned as well as the file names.
+  full.names = T, # Returns relative paths instead of just file names.
+  ignore.case = T)
+
+# Read in source code
+code = unlist(sapply(files, scan, what = 'character', quiet = TRUE))
+
+  # sapply applies a function over a list or vector. It returns a vector or matrix.
+  # In our case it applies the scan function to the list ('files') we created before.
+  # The two arguments thereafter are arguments of the scan function.
+  # scan reads data values. By specifying what = 'character' we indicate that the 
+  # scan function should read character data. And by setting quiet to TRUE, we
+  # prevent a line to be print that indicates how many items have been read.
+  # In our case sapply creates a vector with character values for each of the files in the files object.
+  # By putting the list of vectors returned by sapply into unlist, a single vector
+  # is returned containing all of the character values that were present in the list.
+  # We then store this vector in the object 'code'.
+
+# Retain only source code starting with library
+code <- code[grepl('^library', code, ignore.case=T)]
+code <- gsub('^library[(]', '', code) # Removes 'library(' from the code, only retaining all 'package_name)'.
+code <- gsub('[)]', '', code) # Removes the closing bracket ')' after the package name as well.
+code <- gsub('^library$', '', code)
+
+# retain unique packages
+uniq_packages <- unique(code)
+
+# kick out "empty" package names
+uniq_packages <- uniq_packages[!uniq_packages == ''] 
+
+# order alphabetically
+uniq_packages <- uniq_packages[order(uniq_packages)] 
+
+# Prints required packages
+cat('Required packages: \n')
+cat(paste0(uniq_packages, collapse= ', '),fill=T)
+cat('\n\n\n')
+
+# retrieve list of already installed packages
+installed_packages <- installed.packages()[, 'Package']
+
+# identify missing packages
+to_be_installed <- setdiff(uniq_packages, installed_packages)
+
[…]

### 2024-03-21 src/analysis/regression_analysis.Rmd
removed all install.packages commands from src scripts

# Let's run our analysis! 
## And see how genre prefferences as inferred from average ratings evolve over time

```{r libraries, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(fixest)
library(tidyr)
library(skimr)
library(infer)
library(modelsummary)
library(broom)
library(purrr)
library(viridis)
library(estimatr)
library(pdftools)
```

Let's start with loading the data 
```{r include=FALSE}
mdc <- read_csv("../data_prep/movie_data_cleaned.csv")
```

## basic skeleton model
Let's start with a simple skeleton model and build it from there in gradual steps. So the most basic form is to start regressing all our genres on the average rating. So let's do that!

```{r skeleton model, echo=FALSE}
simple_model <- feols(averageRating ~ drama + romance + war + crime + thriller+ history + comedy + fantasy + adventure + mystery + biography + action + scifi + western + horror + sport + documentary + musical + filmnoir + animation + adult + gameshow + realitytv + talkshow + short + news,
                      data = mdc,
                      split = ~ slide_window_5)
summary(simple_model)
```
So we now have the most basic form of a regression to work with. If you click around a bit you see that within the 5 year time windows some genres become significant, others stay significant and some become insignificant. However, this is the most basic form of a regression and correlational at best. Therefore we are going to extent this formula a bit and see how it evolves to something that may become a little more causal.

## adding fixed effects
### titleType
We are observing behavior over time. But we are currently observing behavior for multiple types of behavior. Or more specifically, for both movies AND series. But these are two different things. So while we still want to know the general genre preference trends, we need to adjust for movie vs. series.

```{r echo=FALSE}
fixed_type_model <- feols(averageRating ~ drama + romance + war + crime + thriller+ history + comedy + fantasy + adventure + mystery + biography + action + scifi + western + horror + sport + documentary + musical + filmnoir + animation + adult + gameshow + realitytv + talkshow + short + news | titleType,
                                data = mdc,
                                split = ~ slide_window_5)

summary(fixed_type_model)
```

If you compare these results against our skeleton model you may see that the standard errors have increased. This is good! this means our analysis has become a little more robust. But let's check our R-squared to be sure.

```{r echo=FALSE}
etable(simple_model)
```

```{r echo=FALSE}
etable(fixed_type_model)
```

Good most of our r-sqaures are improving. This means this added fixed effects was a good one.

### title of movie vs. serie
Next one we want to capture some unobservable effects that are know to the raters but unknown to us. For example, script, plot and actor quality. But also things like music and other elements captured in the series that are outside of the data set.

```{r include=FALSE}
fixed_tt_model <- feols(averageRating ~ drama + romance + war + crime + thriller+ history + comedy + fantasy + adventure + mystery + biography + action + scifi + western + horror + sport + documentary + musical + filmnoir + animation + adult + gameshow + realitytv + talkshow + short + news | titleType,
                                data = mdc,
                                split = ~ slide_window_5)
```

Last, because while out regression assumptions are mostly respected we still may want to increase the robustness of the coefficients. We do this by loosening these assumptions a little, given that heteroscedasticity appears to be a little shady we loosen that assumption a little and then check the R-squared again.

```{r assumptions, echo=FALSE}

fixed_tth_model <- feols(averageRating ~ drama + romance + war + crime + thriller+ history + comedy + fantasy + adventure + mystery + biography + action + scifi + western + horror + sport + documentary + musical + filmnoir + animation + adult + gameshow + realitytv + talkshow + short + news | titleType ,
                                vcov = "hetero",
                                data = mdc,
                                split = ~ slide_window_5)

etable(fixed_tth_model)
```

Good this has a small but positive effect. Now we want to plot the results.

```{r plotting results}

#make a plot that suits

```

### 2024-03-21 gen/paper/paper.Rmd

@@
 In this paper we investigate consumers’ movie and series preferences
-using five of IMDb's datasets containing movie data. First, these
-datasets are loaded, cleaned, inspected, merged and cleaned. Next, the
+using four of IMDb's datasets containing movie data. First, these
+datasets are loaded, inspected, merged and cleaned. Next, the
 data is analyzed using a regression analysis. This regression analysis
-regresses all movie and serie genre's against the average rating's over
+regresses all movie and series genres against the average ratings over
 a period of 5 years. Additionally, the variables title, movieType and
-time are used as control variables to improve the interpret ability of
+time are used as control variables to improve the interpretability of
 the estimates.
@@
 un-nested and then pivoted wider. As a result data with 27 dummies was
-constructed that could assessed separately in the analysis.
+constructed that could be assessed separately in the analysis.
 
@@
 Given that the measurement of genre preferences over time is a construct
-that is viable to many unobservables, fixed effects were added to
-partially capture these unobservant. More specifically the type of title
-(movie vs. series) and title were added. To give an example, it could be
-that for movies, people prefer something with a little more drama than
-they would for a series or vice-versa.
+that is viable to many unobservables, fixed effects were added to the 
+regression analysis to partially capture these unobservables. More 
+specifically the type of title (movie vs. series) and title were added. 
+To give an example, it could be that for movies people prefer something 
+with a little more drama than they would for a series or vice-versa.
 
@@
 movies and series originating from that time may be strongly biased
-because a nice selection of the population may be watching these movies
+because a niche selection of the population may be watching these movies
 in the first place.
@@
 
-Last to see how preferences change over time we build on the assumption
+Last, to see how preferences change over time we build on the assumption
 that if a movie or series is a success they gain many positive ratings
@@
 as a means to calculate behavior over time. Yet, the individual years
-are unlikely to have a remarkable effect on the genre preference trends
+are unlikely to have a remarkable effect on the genre preference trends.
 This is because the effects are so nuanced that they are unlikely to be
-detected. Therefore, to solve this a five-year window was created that
-captures all genre preferences for that period
+detected. Therefore, a five-year window was created that captures all 
+genre preferences for that period of time.
 
@@
 
-While homoskedacity and independence appeared to be moderate at best.
+Homoscedasticity and independence appeared to be moderate at best.
 
@@
 Regardless of these results the decision was made to continue with the
-analysis. This is because the r package fixest allows for modification
+analysis. This is because the R package `fixest` allows for modification
 in the mixed model analysis that helps overcome these limitations. For
@@
 time. Out of all twenty-five genres, only eighteen appeared to
-significantly influence the average ratings on IMBd. These genres were
+significantly influence the average ratings on IMDb. These genres were
 animation, biography, film-noir, fantasy, documentary, crime, comedy,
@@
 \<.01,p~2005-2009~ \<.01), romance (p~1940-1944~ =.03, p~1945-1949~
-\<.01), horror(p~1925-1929~ =.04), game-show(p~2000-2004~ \<.01),
-reality-tv(p~1970-1974~ \<.01), sci-fi(p~1935-1939~ \<.01), and
-shorts(p~1995-1999~ \<.01, p~2005-2009~ \<.01) had a single period
-bursts were they significantly related to the average ratings. Last, the
+\<.01), horror (p~1925-1929~ =.04), game-show (p~2000-2004~ \<.01),
+reality-tv (p~1970-1974~ \<.01), sci-fi (p~1935-1939~ \<.01), and
+shorts (p~1995-1999~ \<.01, p~2005-2009~ \<.01) had a single period
+bursts where they significantly related to the average ratings. Last, the
 genres animation (p\~1940-1944 \<.01, p~1950-1954~ \<.01, p~1975-1979~
 \<.01 -up until 2024), biography (p~1935-1939~ \<.01, p~1985-1989~ \<.01
--Up until 2024), comedy(p~1930-1934~ =.02, p~1950-1954~ =.04,
+-Up until 2024), comedy (p~1930-1934~ =.02, p~1950-1954~ =.04,
 p~1990-1994~ =.01), documentary (p~1930-1934~ \<.01, p\~1945-1949 \<.01,
@@
 (p~1930-1934~ \<.01, p~1935-1939~ \<.01, p~1945-1949~ \<.01,
-p~1970-1974~ =.03), musical(p~1960-1964~ =.09, p~1985-1989~ =.03,
-p~1990-1994~ =.02, p~2020-2024~\<.01), and war(p~1930-1934~ =.02,
+p~1970-1974~ =.03), musical (p~1960-1964~ =.09, p~1985-1989~ =.03,
+p~1990-1994~ =.02, p~2020-2024~\<.01), and war (p~1930-1934~ =.02,
 p~1945-1949~ \<.01, p~1960-1964~ =.04 up to and including p~1970-1974~
 \<.01, p~1985-1989~ \<.01 up to and including p~2005-2009~ \<.01)
-significantly were related to the average rating in burst with unrelated
-periods in between
+were significantly related to the average ratings in bursts with unrelated
+periods in between.
 
@@
 For genres like war and film-noir the correlation could be a sign of the
-times, and strongly guided by biases in the rating population. For
+times, and can be strongly guided by biases in the rating population. For
 example, when the genre war was indicated to be significantly related to
@@
 may like to watch propaganda movies from that time. As a result, the
-average ratings are higher because a nice of interested people is
+average ratings are higher because a niche of interested people is
 watching. Similar to film-noir, people who are interested in this type
@@
 thriller, and western are all insignificant and do not appear to be
-correlated to the average ratings on IMBd. A reason for this may be that
+correlated to the average ratings on IMDb. A reason for this may be that
 these elements have become expected or core components of movies and
@@
 This research illustrates that genre preferences may be related to the
-average IMBd ratings and vary over time. While further research is
+average IMDb ratings and vary over time. While further research is
 necessary to fine-tune these claims the current research does provide
@@
 shows that the common ingredients like romance and action may not stand
-out as much as biography and history might. Additionally, the results
-showed that The results of this analysis can be, at best, interpreted as
-correlational given the vast amount of assumptions and potential hidden
-dangers of sampling biases (e.g., film-noir and war genres). While this
-has been partially mitigated by loosening some of the underlying
-assumptions and adding fixed effects, the fact remains that these appear
-as trend observations. Therefore, the results do not necessarily
-conclude that some genres lead to higher average ratings. However, the
-results do indicate that there may be preferences over time that may
-lead to higher average ratings.
+out as much as biography and history might. 
+The results of this analysis can be, at best, interpreted as correlational 
+given the vast amount of assumptions and potential hidden dangers of 
+sampling biases (e.g., film-noir and war genres). While this has been 
+partially mitigated by loosening some of the underlying assumptions and 
+adding fixed effects, the fact remains that these appear as trend 
+observations. Therefore, the results do not necessarily conclude that some 
+genres lead to higher average ratings. However, the results do indicate that 
+there may be preferences over time that may lead to higher average ratings.
 
@@
 more can be learned and investigated. Here are three ways in which the
-current research into how genres relate to average IMBd rating may be
+current research into how genres relate to average IMDb rating may be
 extended:
@@
 Second, researchers may benefit by including data from multiple sources.
-Currently, the analysis is limited to IMBd data but there are also other
-sources such as rottentomato's for example. By combining these data sets
+Currently, the analysis is limited to IMDb data but there are also other
+sources such as Rotten Tomatoes for example. By combining these data sets
 the interpretation of the results becomes less biased by the data
 platform. For example, it may be that people of higher age groups
-typically review IMBd, and younger groups adopt commentators. By
+typically review on IMDb, and younger groups adopt commentators. By
 broadening the data sources the generalization of the results increases.

### 2024-03-22 src/analysis/regression_analysis.R
added install.stargazer to regression_analysis

@@ -9,6 +9,7 @@ install.packages("modelsummary")
 install.packages("broom")
 install.packages("purrr")
 install.packages("estmatr")
+install.packages("stargazer")
 
 library(tidyverse)
 library(fixest)

### 2024-03-22 src/analysis/regression_analysis.Rmd

@@
+---
+output:
+  pdf_document: default
+  html_document: default
+---
 # Let's run our analysis! 
@@
 library(fixest)
-library(tidyr)
 library(skimr)
@@
 But we are currently observing behavior for multiple types of behavior.
-Or more specifically, for both movies AND series.
+Or more speicifally, for both movies AND series.
 But these are two different things.
-So while we still want to know the general genre preference trends, we need to adjust for movie vs.
+So while we still want to know the general genre prefference trends, we need to adjust for movie vs.
 series.
@@
 this means our analysis has become a little more robust.
-But let's check our R-squared to be sure.
+But let's check our r-sqaured to be sure.
 
 ```{r echo=FALSE}
-etable(simple_model)
+coeftable(simple_model)
 ```
@@
 ```{r echo=FALSE}
-etable(fixed_type_model)
+coeftable(fixed_type_model)
 ```
@@
 Last, because while out regression assumptions are mostly respected we still may want to increase the robustness of the coefficients.
-We do this by loosening these assumptions a little, given that heteroscedasticity appears to be a little shady we loosen that assumption a little and then check the R-squared again.
+We do this by loosening these assumptions a little, given that hetroskedacity appears to be a little shady we loosen that assumption a little and then check the r sqaured again.
 
@@
 
-etable(fixed_tth_model)
+coeftable(fixed_tth_model)
 ```
@@
 ```{r plotting results}
+coefplot(fixed_tth_model)
+```
+As you can see from the plot some genres, such as romance, are largely significant are nicely consistent over the years.
+However, genres such as game-shows or news (which only rose after the 2000's) do not have observations for all years and the observations that are there are remarkably volatile given their large confidence intervals.
 
-#make a plot that suits
+Next we want to see how a specific genre evolves over the years.
+
+```{r}
+list_of_coeficients <- coef(fixed_tth_model) %>%
+  select(-id, -sample.var)
+
+list_of_standard_deviations <- se(fixed_tth_model) %>%
+  select(-id,-sample.var)
+
+list_of_coeficients_long <- list_of_coeficients %>%
+  pivot_longer(cols = -sample, names_to = "genre", values_to = "coef_value") %>%
+
+# Pivot standard deviations longer
+list_of_standard_deviations_long <- list_of_standard_deviations %>%
+  pivot_longer(cols = -sample, names_to = "genre", values_to = "std_dev_value")
+
+# Calculate p_threshold for each genre
+graph_data <- left_join(list_of_coeficients_long, list_of_standard_deviations_long, by = "sample") %>%
+  mutate(across(c(genre.x, genre.y), as.factor)) %>% 
+  filter(genre.x == genre.y) %>%
+  mutate(p_threshold = coef_value / std_dev_value,
+         p_significance = ifelse(p_threshold > 1.96, 1, 0))
+
+conf_level <- 0.95
+z_value <- qnorm((1 + conf_level) / 2)
+
+# Calculate confidence intervals
+graph_data <- graph_data %>%
+  mutate(
+    lower_ci = coef_value - z_value * std_dev_value,
+    upper_ci = coef_value + z_value * std_dev_value
+  )
+
+graph_data <- graph_data %>%
+  drop_na()
+
+# Plot with confidence intervals
+ggplot(graph_data, aes(x = sample, y = coef_value, color = factor(p_significance))) +
+  geom_point() +
+  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2) +
+  scale_color_manual(values = c("red", "green")) +
+  xlab("Estimates") + ylab("Years") + facet_wrap(~genre.x) +
+  scale_x_discrete(breaks = unique(graph_data$sample)[seq(1, length(unique(graph_data$sample)), length.out = 4)])
+```
+
+As you can see some genres are never significant, e.g., sports and thriller.
+While others become significant and never stop, e.g., history.
+There are also speaks in genres like war, where it seems to be falling in and out of favor.
+```{r}
 

### 2024-03-22 src/analysis/app.R
made a shiny app

@@ -1,0 +1,84 @@
+library(shiny)
+library(tidyverse)
+library(fixest)
+library(tidyr)
+library(skimr)
+library(infer)
+library(modelsummary)
+library(broom)
+library(purrr)
+library(viridis)
+library(estimatr)
+library(pdftools)
+
+# Define UI
+ui <- fluidPage(
+  titlePanel("Genre Preferences Analysis"),
+  mainPanel(
+    fluidRow(
+      column(6,
+             selectInput("genre_1", "Select Genre 1:", choices = unique(graph_data$genre.x)),
+             plotlyOutput("plot_output_1")
+      ),
+      column(6,
+             selectInput("genre_2", "Select Genre 2:", choices = unique(graph_data$genre.x)),
+             plotlyOutput("plot_output_2")
+      )
+    ),
+    br(),
+    p("Hover over a dot in the plot to see the exact value of the estimate, and click on the significance value on the index on the right to filter on significance.")
+  )
+)
+
+# Define server logic
+server <- function(input, output, session) {
+  # Render the plots
+  output$plot_output_1 <- renderPlotly({
+    selected_genre_data <- reactive({
+      filtered_data <- graph_data %>%
+        filter(genre.x == input$genre_1)
+      return(filtered_data)
+    })
+    
+    p <- ggplot(selected_genre_data(), aes(x = as.factor(sample), y = coef_value, color = factor(p_significance))) +
+      geom_point() +
+      geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2) +
+      scale_color_manual(values = c("red", "green"), 
+                         labels = c("Insignificant", "Significant")) +
+      xlab("Year") + ylab("Coefficient Value") + ggtitle(paste("Genre:", input$genre_1)) +
+      theme_minimal() +
+      theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+      guides(color = guide_legend(title = "Significance"))
+    
+    # Convert ggplot to plotly
+    ggplotly(p, tooltip = c("x", "y"), click = "plot_click")
+  })
+  
+  output$plot_output_2 <- renderPlotly({
+    selected_genre_data <- reactive({
+      filtered_data <- graph_data %>%
+        filter(genre.x == input$genre_2)
+      return(filtered_data)
+    })
+    
[…]

### 2024-03-22 gen/paper/paper.Rmd
plots and pdfs

--- 2024-03-18 gen/paper/paper.Rmd
@@
 
-The entertainment industry is a dynamic industry. Consumer preferences
-continuously change, and new movies and series are continuously being
-produced. Genre continues to be an important topic in the entertainment
-industry. Genre preferences indicate what consumers liked to watch in
-the past, and therefore probably also would like to watch in the future.
-Thus, genre can serve as a selection criteria, based on which consumers
-decide whether to watch a certain movie or not. Therefore, an
-understanding of genre preferences gives movie producers a direction on
-what type of genre they should adopt to increase chances of success and
-to best deliver the message they want to bring across. Consequently, it
-is important to investigate the evolution of consumers’ genre
-preferences over time.
+The entertainment industry is highly dynamic. Consumer preferences keep
+changing, and new movies and series are produced regularly. These
+changes in preferences require the industry to respond accordingly. For
+example, showing an ankle in a movie might have been considered
+scandalous in the 1950s, but it is now just a minor detail. To make an
+impact in such an ever-evolving industry, movie directors need to get
+creative. These changes in the industry influence how movies and series
+are produced and how consumers react to them. One way to understand
+these patterns is by examining the genre of a product.
+
+Genre preferences reflect what consumers have enjoyed watching in the
+past, and hence are likely to enjoy in the future. Therefore, genre can
+be used as a criterion for selecting productions, based on which
+consumers decide whether to watch a particular production or not. An
+understanding of genre preferences provides filmmakers with guidance on
+which genre to choose to increase the chances of success and to best
+convey their intended message. However, the nature of genres is
+constantly evolving, and it is important to comprehend how current
+consumers respond to the evolution of a genre over time. For instance,
+an action movie today might have rapid scene changes, multiple plot
+twists, and lengthy fight scenes, but on average, such movies may only
+receive moderate ratings at best. In contrast, action movies from two
+decades ago had a more gradual plot development and were less
+overwhelming, yet they received a higher average rating. When consumers
+rely on the genre productions of the past to make their choice, it may
+adversely impact their evaluation of a current production in the same
+genre.
+
+In order to gain a better understanding of how modern consumers rate
+products and services, it is crucial to comprehend how they use their
+past preferences as a point of reference. Hence, this research paper
+aims to explore whether there exist any discernible patterns in genre
+preferences over time, and whether some genres tend to have a greater
+impact on average ratings than others.
 
@@
 
-**How do consumers' movie genre preferences change over time?**
+**How do consumers' production preferences of genre elements change over
+time, and how do they impact the average ratings of those same
+productions?**
+
+## Relevance
+
+The research results shed light on how consumers use dynamic genres to
+shape their satisfaction with a movie or TV series. The findings suggest
+that some genres are preferred in certain years over others. For
+example, war movies tend to receive higher ratings during world wars
+compared to times of peace. This implies that consumers use these
+productions as references to rate them in context of the sign of the
+times. Managers may want to consider adjusting their productions to
+better suit the elements in those preferred years.
+
+The study also found that recent fantasy movies tend to receive lower
+ratings from consumers, while those produced in the 70s are rated more
+favorably. Overall, the results suggest that managers may face
+challenges in meeting previously set expectations and that these
+findings provide a reference frame for when those expectations are met.
+
+Additionally, the results also provide insights into how genres are
+related to average ratings across another. Currently, every production
+has a similar pattern of ingredients. Most movies contain hints of drama
+and romance. Whether it is in a distropian sci-fi survival movie or an
+horror action series. However, the results indicated that these common
+genres are not significantly related to the average ratings. In contrast
+some movies and series do contain unique elements do results in
+significant relationships. For example, biographies and animations. This
+may imply that consumers may not rely so heavily on past genres that are
+common because they gradually change with times without consumers
+noticing. (Think of it like a birthday party with your family when you
+are 12. Your aunt keeps telling you "How much you have grown!", but you
+don't notice any difference) In contrast, the uniqueness of biographies
+does sharply stand out. Therefore, managers may want to focus more
+strongly on the less common genre features compared to more common ones.
 
@@
 In this paper we investigate consumers’ movie and series preferences
-using five of IMDb's datasets containing movie data. First, these
+using four of IMDb's datasets containing movie data. First, these
 datasets are loaded, cleaned, inspected, merged and cleaned. Next, the
 data is analyzed using a regression analysis. This regression analysis
-regresses all movie and serie genre's against the average rating's over
-a period of 5 years. Additionally, the variables title, movieType and
-time are used as control variables to improve the interpret ability of
-the estimates.
+regresses all movie and series genre's against the average rating's over
+a sliding period of 5 years. Additionally, the variables title,
+movieType and time are used as control variables to improve the
+interpret ability of the estimates.
 
@@
 in Analysis |
-|------------------|------------------------------------------------------------------------------------------------------------------------------------------------------------------|------------------------|
+|------------|-------------------------------------------------|------------|
 | Average Rating   | The average rating on IMBd per title of a given movie or series.
@@
 
-### Average Movie Rating
+### Outcome Variable: Average Movie Rating
 
@@
 
-### Genres
+### Explanatory Variable: Genres
 
@@
 ## Results and Discussion
+
 ```{r}
@@
 analysis results become more reliable.
+
+```{r}
+
+```

### 2024-03-22 gen/paper/paper.Rmd

--- 2024-03-21 gen/paper/paper.Rmd
@@
 using four of IMDb's datasets containing movie data. First, these
-datasets are loaded, inspected, merged and cleaned. Next, the
+
+datasets are loaded, cleaned, inspected, merged and cleaned. Next, the
 data is analyzed using a regression analysis. This regression analysis
-regresses all movie and series genres against the average ratings over
-a period of 5 years. Additionally, the variables title, movieType and
-time are used as control variables to improve the interpretability of
-the estimates.
+regresses all movie and series genre's against the average rating's over
+a sliding period of 5 years. Additionally, the variables title,
+movieType and time are used as control variables to improve the
+interpret ability of the estimates.
 

### 2024-03-22 src/analysis/regression_analysis.Rmd

--- 2024-03-21 src/analysis/regression_analysis.Rmd
@@
 ```{r libraries, message=FALSE, warning=FALSE, include=FALSE}
+install.packages("tidyverse")
+install.packages("fixest")
+install.packages("tidyr")
+install.packages("skimr")
+install.packages("infer")
+install.packages("modelsummary")
+install.packages("broom")
+install.packages("purrr")
+install.packages("estmatr")
+install.packages("pdftools")
+
 library(tidyverse)
@@
 this means our analysis has become a little more robust.
-But let's check our R-squared to be sure.
+But let's check our r-sqaured to be sure.
 

### 2024-03-22 src/data_prep/data_prep.Rmd

@@
 # Cleaning the Data
-So after retrieving and mergig our data directly form the IMBD site, we now need to chcek and clean the data. In this markdown the data set is cleaned, reformatted and restructured.
+So after retrieving and mergig our data directly form the IMBD site, we now need to check and clean the data. In this markdown the data set is cleaned, reformatted and restructured.
 
-```{r libraries, message=FALSE, warning=FALSE}
+```{r libraries, message=FALSE, warning=FALSE, include=FALSE}
 install.packages("tidyverse")
@@
 
-```{r reformatting the data, message=FALSE, warning=FALSE}
-movie_data <- read_csv(movie_data)
+```{r reformatting the data, message=FALSE, warning=FALSE, include=FALSE}
+movie_data <- read_csv("movie_data.csv")
 
 movie_data <- movie_data %>%
-  mutate(across(c(tconst, directors, writers, titleType, isAdult,genres, parentTconst,isOriginalTitle, types, originalTitle), as.factor)) %>%
+  mutate(across(c(tconst, titleType, isAdult,genres, parentTconst,isOriginalTitle, types, originalTitle), as.factor)) %>%
   mutate(across(c(averageRating,numVotes,runtimeMinutes, title, seasonNumber, episodeNumber), as.numeric)) 
-
 ```
 
-First, let's think about some operalization basics. Or more specifically, the operalization of our variables.
+First, let's think about some operalization basics. Or more specifically, the operalization of the variables.
 
 ## starting with out DV: ratings
-```{r Raw DV print}
+```{r Raw DV print, echo=FALSE}
 print(summary(movie_data$averageRating))
@@
 
-Okay. So the scale is okay BUT remember that these are AVERAGE ratings, and that on average ratings 1 and 10 are quite extreem and frankly, unrealistic.
+Okay. So the scale is okay BUT remember that these are AVERAGE ratings, and that on average ratings 1 and 10 are quite extreme and frankly, unrealistic.
 
@@
 
-```{r DV plots, message=FALSE, warning=FALSE}
+```{r DV plots, echo=FALSE, message=FALSE, warning=FALSE}
 ggplot((movie_data), aes(x = averageRating)) +
@@
 
-```{r}
+```{r echo=FALSE, message=FALSE, warning=FALSE}
 ggplot(movie_data, aes(x = averageRating)) +
@@
 ```
+
 As you can see there appears to be a normal distribution that is slightly skewed to the left.
-If you think logically about this this may be a result from the number of reviews given as opposed to the actual rating
+If you think logically about this, it may be a result from the number of reviews given as opposed to the actual rating
 
-```{r DV vs NumVotes, message=FALSE, warning=FALSE}
+```{r DV vs NumVotes, echo=FALSE, message=FALSE, warning=FALSE}
 print(summary(movie_data$numVotes))
@@
 
-Do you see how the average movie only has 106 votes? Or even 5! that will defiantely influence the average
+Do you see how the average movie only has 106 votes? Or even 5! That influences the averages.
 
-```{r Plot DV and numVotes, message=FALSE, warning=FALSE}
+```{r Plot DV and numVotes, echo=FALSE, message=FALSE, warning=FALSE}
 ggplot(movie_data, aes(x = numVotes)) +
@@
 print(table(movie_data$numVotes_group))
-````
+```
 
 Okay, so let's filter some of there observations out.
-These observations are not deleted.
-But they are simply left behind in the corner.
 We want reliable data and these observation are unlikely to be reliable.
-But instead of arbritarily unselecting stuff we should plot the data and see where some issues lie.
+But instead of arbitrarily unselecting observations we should plot the data and see where some issues lie.
 
-```{r Filtering DV, message=FALSE, warning=FALSE}
-
+```{r Filtering DV, echo=FALSE, message=FALSE, warning=FALSE}
 below_100 <- movie_data %>%
@@
 
-```{r}
+```{r include=FALSE, paged.print=TRUE}
 movie_data <- movie_data %>%
@@
 Now that we have cleaned our DV. let's look at our IV's. First are some basic decisions. Movies are presented multiple times, in multiple countries. So we want to filter on the original title.
-```{r}
+
+```{r include=FALSE}
 movie_data <- movie_data %>%
@@
 series.
-This is because we  aren interested in generes, and those may be dependent on wether it is a movie vs.
-series.
+This is because we are interested in genres, and those may be dependent on whether a title it is a movie or a series (e.g., news).
 But we also want to see if we can solve some missing values and drop some irrelevant columns about attributes.
 
-```{r}
+```{r include=FALSE}
 movie_data<- movie_data %>% 
@@
 
+drop_columns <- c("attributes", "region", "language", "isOriginalTitle", "parentTconst", "episodeNumber", "seasonNumber", "title", "originalTitle")
+
 movie_data <- movie_data %>%
-  mutate(movie_dummy = ifelse(str_detect(titleType, regex("movie", ignore_case = TRUE)), 1, 0),
-         newfilm_dummy = ifelse(startYear > 1999, 1, 0),
-         above_avg = ifelse(averageRating > mean(averageRating), 1, 0),
-         drama_dummy = ifelse(str_detect(genres, regex("drama", ignore_case = TRUE)), 1, 0)) %>%
+  mutate(movie_dummy = as.integer(str_detect(titleType, regex("movie", ignore_case = TRUE))),
+         newfilm_dummy = as.integer(startYear > 1999),
+         above_avg = as.integer(averageRating > mean(averageRating, na.rm = TRUE)),
+         drama_dummy = as.integer(str_detect(genres, regex("drama", ignore_case = TRUE)))) %>%
   filter(drama_dummy == 1) %>%
-  select(-attributes, -ordering, -region, -language, -isOriginalTitle, -parentTconst, -episodeNumber, -seasonNumber, -title, -originalTitle)
+  select(-all_of(drop_columns))
 
@@
 Therefore, we construct a window that captures 5 years of viewer patterns.
-Because we do not know how these averRating votes we dynamic over time (for series), we assume that the yearStart is the year in which the most number of votes (numVotes) are generated.
-This is logical, because if this is positive the series will be continued, and if the reveiws are negative the series will be liekly to be discontinued.
-How the rating drops as the perc quality of the series drops over time, is for the orupose of this study left out of the equation.
+Because we do not know how these averRating votes dynamicly evolve over time (for series), we assume that the yearStart is the year in which the most number of votes (numVotes) are generated.
+This is logical, because if the average rating is positive the series will be continued, and if the reviews are negative the series will be likely to be discontinued.
+How the rating drops as the perceived quality of the series drops over time, is for the purpose of this study, left out of the equation.
 
-```{r}
+```{r echo=FALSE}
 movie_data <- movie_data %>%
@@
 
-```{r}
+```{r include=FALSE}
 movie_data <- movie_data %>%
@@
 First, we look at how number of votes and rating behave for each genre.
-```{r}
+
+```{r echo=FALSE}
 ggplot(movie_data, aes(x = numVotes, y = averageRating, color= genres)) +
@@
 ```
+
 As you can see there is only a very small patern there.
@@
 
-Let's see how the actual ratings are then distrubuted across genres
-```{r}
-
+Let's see how the actual ratings are then distributed across genres
+```{r echo=FALSE}
 ggplot(movie_data, aes(averageRating, color= genres))+
@@
 
-```{r}
+```{r echo=FALSE}
 ggplot(movie_data, aes(sample = averageRating, color = genres)) +
@@
 
-```{r}
+```{r echo=FALSE}
 residuals <- movie_data$averageRating - mean(movie_data$averageRating)
@@
   geom_point() +
-  geom_smooth(method = "loess", se = FALSE) +  # Add a smooth line to visualize any patterns
-  labs(x = "Fitted Values", y = "Residuals") +  # Add axis labels
-  ggtitle("Residuals vs. Fitted Values")  # Add a plot title
+  geom_smooth(method = "loess", se = FALSE) +  patterns
+  labs(x = "Fitted Values", y = "Residuals") +  
+  ggtitle("Residuals vs. Fitted Values")  
 ```
@@
 
-```{r}
-
+```{r echo=FALSE}
 # Calculate residuals
@@
 
-Linearity looks chaotics but okay.
+Linearity looks chaotic but okay.
 It may be a little smaller on the left and increases to the right but this is very little.
-So last, linearity.
+So we move on the last assumption, linearity.
 This is tricky, because there is no reason for genre to lead to a higher or lower rating.
@@
 
-```{r}
+```{r echo=FALSE}
 ggplot(movie_data, aes(x = slide_window_5, y = averageRating)) +
@@
 Okay well that not real linear. There is some trend though. So we are going to continue with out analysis.
+
 However Let's clean the data set a little so each genre is a neat dummy.
 
-```{r}
+```{r include=FALSE}
 movie_data <- movie_data %>%
@@
   pivot_wider(names_from = genres, values_from = genre_dummy, values_fill = list(genre_dummy = 0)) %>%
-  rename(scifi = `sci-fi`) %>%
-  rename(filmnoir = `film-noir`) %>%
-  rename(gameshow = `game-show`) %>%
-  rename(realitytv = `reality-tv`) %>%
-  rename(talkshow = `talk-show`)
-
+   rename(
+    scifi = `sci-fi`,
+    filmnoir = `film-noir`,
+    gameshow = `game-show`,
+    realitytv = `reality-tv`,
+    talkshow = `talk-show`
+  )
 ```
@@
 Don't leave before saving!
+
 ```{r save file}

### 2024-03-22 src/data_prep/getting_the_data.R
fixed typo in episodes

@@ -26,7 +26,7 @@ akas <- akas %>%
   mutate(tconst = titleId) %>%
   select(-titleId)
 
-episodes <- episodes %>%
+episode <- episode %>%
   mutate(across(episodeNumber, as.numeric)) %>% 
   mutate(across(seasonNumber, as.numeric))
 
@@ -42,3 +42,4 @@ movie_data <- Reduce(function(x, y) left_join(x, y, by = join_column), data_sets
 
 #now let's store the data
 write_csv(movie_data, "src/data_prep/movie_data.csv")
+

### 2024-03-22 src/analysis/regression_analysis.R
removed unnecassary .R files in src

@@ -1,68 +1,0 @@
-#In this file perform the analysis on the cleaned data from SRC/Data_Prep/Data_prep.R
-
-install.packages("tidyverse")
-install.packages("fixest")
-install.packages("tidyr")
-install.packages("skimr")
-install.packages("infer")
-install.packages("modelsummary")
-install.packages("broom")
-install.packages("purrr")
-install.packages("estmatr")
-
-library(tidyverse)
-library(fixest)
-library(tidyr)
-library(skimr)
-library(infer)
-library(modelsummary)
-library(broom)
-library(purrr)
-library(viridis)
-library(estimatr)
-library(stargazer)
-
-#input
-mdc <- read_csv("src/data_prep/movie_data_cleaned.csv")
-
-
-
-#let's start with the most basic skeleton
-fixed_type_model <- feols(averageRating ~ drama + romance + war + crime + thriller+ history + comedy + fantasy + adventure + mystery + biography + action + scifi + western + horror + sport + documentary + musical + filmnoir + animation + adult + gameshow + realitytv + talkshow + short + news | titleType,
-                          data = mdc,
-                          split = ~ slide_window_5)
-
-summary(fixed_type_model)
-
-
-#now we add some fixed effects that capture inherent information we may not know changes
-fixed_tt_model <- feols(averageRating ~ drama + romance + war + crime + thriller+ history + comedy + fantasy + adventure + mystery + biography + action + scifi + western + horror + sport + documentary + musical + filmnoir + animation + adult + gameshow + realitytv + talkshow + short + news | titleType,
-                        data = mdc,
-                        split = ~ slide_window_5)
-
-summary(fixed_tt_model)
-
-#adjust model to the current assumptions
-fixed_tth_model <- feols(averageRating ~ drama + romance + war + crime + thriller+ history + comedy + fantasy + adventure + mystery + biography + action + scifi + western + horror + sport + documentary + musical + filmnoir + animation + adult + gameshow + realitytv + talkshow + short + news | titleType ,
-                        vcov = "hetero",
-                        data = mdc,
-                        split = ~ slide_window_5)
-
-etable(fixed_tth_model)
-#################################################################################
-
-# Create a list named "genres"
-genres <- list(
-  "drama", "romance", "war", "crime", "thriller",
-  "history", "comedy", "fantasy", "adventure", "mystery",
-  "biography", "action", "scifi", "western", "horror",
[…]

### 2024-03-22 src/data_prep/data_prep.R

@@ -1,70 +1,0 @@
-install.packages("tidyverse")
-install.packages("tidyr")
-install.packages("dplyr")
-install.packages("stringr")
-
-library(tidyverse)
-library(tidyr)
-library(dplyr)
-library(stringr)
-
-#input
-movie_data <- read_csv("src/data_prep/movie_data.csv")
-
-#clean raw data
-movie_data <- movie_data %>%
-  mutate(across(c(tconst, titleType, isAdult, genres, parentTconst,isOriginalTitle, types, originalTitle), as.factor)) %>%
-  mutate(across(c(averageRating,numVotes,runtimeMinutes, title, seasonNumber, episodeNumber), as.numeric)) 
-
-#filter on original title
-movie_data <- movie_data %>% filter(numVotes> 100) %>%
-  filter(isOriginalTitle== 1) %>%
-  distinct(primaryTitle, .keep_all = TRUE) 
-
-#filter for movies and series
-movie_data<- movie_data %>% 
-  filter(titleType %in% c("movie", "tvMovie", "tvMiniSeries", "tvSeries"))
-
-#reformat columns and drop irrelevant ones
-movie_data <- movie_data %>%
-  mutate(movie_dummy = ifelse(str_detect(titleType, regex("movie", ignore_case = TRUE)), 1, 0),
-         newfilm_dummy = ifelse(startYear > 1999, 1, 0),
-         above_avg = ifelse(averageRating > mean(averageRating), 1, 0),
-         drama_dummy = ifelse(str_detect(genres, regex("drama", ignore_case = TRUE)), 1, 0)) %>%
-  filter(drama_dummy == 1) %>%
-  select(-attributes, -ordering, -region, -language, -isOriginalTitle, -parentTconst, -episodeNumber, -seasonNumber, -title, -originalTitle)
-
-#make a beter targetted data file
-movie_data <- movie_data %>%
-  select(tconst, averageRating,numVotes, titleType, startYear, runtimeMinutes, genres)
-  
-#make a window for analysis
-slide_window <- movie_data %>%
-  group_by(startYear) %>%
-  count()
-
-movie_data <- movie_data %>%
-  filter(startYear >= 1925) %>%
-  mutate(slide_window_5 = cut(startYear, breaks = seq(1925, 2025, by = 5), labels = paste(seq(1925, 2020, by = 5), "-", seq(1929, 2024, by = 5)), include.lowest = TRUE))
-
[…]

### 2024-03-22 src/data_prep/data_prep.Rmd
fixed typo

@@
 ```{r libraries, message=FALSE, warning=FALSE, include=FALSE}
-install.packages("tidyverse")
-install.packages("tidyr")
-install.packages("dplyr")
-install.packages("stringr")
-
 library(tidyverse)
@@
   geom_point() +
-  geom_smooth(method = "loess", se = FALSE) +  patterns
+  geom_smooth(method = "loess", se = FALSE) + 
   labs(x = "Fitted Values", y = "Residuals") +  
@@
   facet_wrap(~genres)
-````
+```
 

### 2024-03-22 src/analysis/regression_analysis.Rmd

--- 2024-03-22 src/analysis/regression_analysis.Rmd
@@
 But we are currently observing behavior for multiple types of behavior.
-Or more speicifally, for both movies AND series.
+Or more specifically, for both movies AND series.
 But these are two different things.
-So while we still want to know the general genre prefference trends, we need to adjust for movie vs.
+So while we still want to know the general genre preference trends, we need to adjust for movie vs.
 series.
@@
 this means our analysis has become a little more robust.
-But let's check our r-sqaured to be sure.
+But let's check our R-squared to be sure.
 
@@
 Last, because while out regression assumptions are mostly respected we still may want to increase the robustness of the coefficients.
-We do this by loosening these assumptions a little, given that hetroskedacity appears to be a little shady we loosen that assumption a little and then check the r sqaured again.
+We do this by loosening these assumptions a little, given that heteroscedasticity appears to be a little shady we loosen that assumption a little and then check the R-squared again.
 

### 2024-03-22 src/data_prep/data_prep.Rmd

@@
 # Cleaning the Data
-So after retrieving and mergig our data directly form the IMBD site, we now need to check and clean the data. In this markdown the data set is cleaned, reformatted and restructured.
+So after retrieving and merging our data directly form the IMBD site, we now need to check and clean the data. In this markdown the data set is cleaned, reformatted and restructured.
 
@@
 
-First, let's think about some operalization basics. Or more specifically, the operalization of the variables.
+First, let's think about some operationalization basics. Or more specifically, the operationalization of the variables.
 
@@
 
-Okay, so it looks like there is some normal distribution. How about homoskedacity?
+Okay, so it looks like there is some normal distribution. How about homoscedasticity?
 
@@
   geom_point() +
-  geom_smooth(method = "loess", se = FALSE) + 
+  geom_smooth(method = "loess", se = FALSE) +  patterns
   labs(x = "Fitted Values", y = "Residuals") +  
@@
 
-Okay well that not real linear. There is some trend though. So we are going to continue with out analysis.
+Okay well that is not really linear. There is some trend though. So we are going to continue with our analysis.
 
-However Let's clean the data set a little so each genre is a neat dummy.
+However, let's clean the data set a little so each genre is a neat dummy.
 

### 2024-03-22 src/analysis/regression_analysis.Rmd
retrieved missing graphs

--- 2024-03-22 src/analysis/regression_analysis.Rmd
@@
 ```{r libraries, message=FALSE, warning=FALSE, include=FALSE}
-install.packages("tidyverse")
-install.packages("fixest")
-install.packages("tidyr")
-install.packages("skimr")
-install.packages("infer")
-install.packages("modelsummary")
-install.packages("broom")
-install.packages("purrr")
-install.packages("estmatr")
-install.packages("pdftools")
-
 library(tidyverse)
@@
 ```{r plotting results}
+#getting the coefficients
+list_of_coeficients <- coef(fixed_tth_model)
+#getting
+list_of_standard_deviations <- se(fixed_tth_model)
 
-#make a plot that suits
+# Pivot coefficients longer
+list_of_coeficients_long <- list_of_coeficients %>%
+  select(!c(sample.var, id)) %>%
+  pivot_longer(cols = c(-sample), names_to = "genre", values_to = "coef_value")
+
+# Pivot standard deviations longer
+list_of_standard_deviations_long <- list_of_standard_deviations %>%
+  select(!c(sample.var, id)) %>%
+  pivot_longer(cols = -sample, names_to = "genre", values_to = "std_dev_value")
+
+graph_data <- left_join(list_of_coeficients_long, list_of_standard_deviations_long, by = c("sample", "genre"))
+
+#confidence level, let's say 95%
+conf_level <- 0.95
+z_value <- qnorm((1 + conf_level) / 2)
+
+graph_data <- graph_data %>%
+  drop_na(coef_value) %>%
+  mutate(   lower_ci = coef_value - z_value * std_dev_value,
+    upper_ci = coef_value + z_value * std_dev_value,
+    p_threshold = coef_value / std_dev_value,
+    p_significance = ifelse(p_threshold > 1.96, 1, 0))
+
+ggplot(graph_data, aes(x = sample, y = coef_value, color = factor(p_significance))) +
+  geom_point() +
+  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2) +
+  scale_color_manual(values = c("red", "green")) +
+  xlab("Estimates") + ylab("Years") +
+  facet_wrap(~ genre)
 
 ```
+
+```{r saving the doc}
+#insert pdf knit path
+```

### 2024-03-23 src/data_prep/data_prep.Rmd
change file location for outputs

@@
 ```{r reformatting the data, message=FALSE, warning=FALSE, include=FALSE}
-movie_data <- read_csv("movie_data.csv")
+movie_data <- read_csv("data/movie_data.csv")
 
@@
 ```{r save file}
-write_csv(movie_data, "movie_data_cleaned.csv")
+write_csv(movie_data, "data/movie_data_cleaned.csv")
 ```

### 2024-03-23 src/data_prep/getting_the_data.R

@@ -41,5 +41,5 @@ movie_data <- Reduce(function(x, y) left_join(x, y, by = join_column), data_sets
 #Awesome! Now we have running code that builds an entire dataframe from seperate ones.
 
 #now let's store the data
-write_csv(movie_data, "src/data_prep/movie_data.csv")
+write_csv(movie_data, "data/movie_data.csv")
 

### 2024-03-23 src/data_prep/data_prep.Rmd
added descriptives to data_prepRMD and fixed a bit of the descriptives structure

@@
 
-## starting with out DV: ratings
+## starting with out DV: ratings variable are defined as averageRating and should be between 1 and 10.
 ```{r Raw DV print, echo=FALSE}
@@
 
+The mean of the averageRating variable is 6.6.
+
+```{r DV scale, echo=FALSE}
 Okay. So the scale is okay BUT remember that these are AVERAGE ratings, and that on average ratings 1 and 10 are quite extreme and frankly, unrealistic.
@@
 ```
+Now that we have filtered the number of votes of each film to be more than 100, Films now have on average 24500 votes.
 
@@
 
+We also have created a dummy variable called above_avg which indicates whether a film has a rating above or below average.
+
 ```{r include=FALSE}
@@
 ```
+After filtering to only series and movies, we end up with 120273 movies and 27722 series.
 
@@
 ```
+We have filtered the data set to only include movies and series that have been released after 1925.
 
@@
 ```
+After all the filtering, we have 70087 films left in our data set. From this number, 60246 are movies and 9841 are series. The resulting standard deviation for the total of films is 1.12. 
+In the period from 2015 until 2019, the most amount of films were released being 11353, 2019 was the year with the biggest amount of releases, 2586 films.
+On the other hand, 1926 the least amount of films were released on IMDB, 54 films.
+The average number of votes in the final dataset was 7146.
+In terms of runtime, the films are on average 101 minutes long.
+The average ratings of the films in our final data set is 6.3, the lowest rating noted as 1 and the highest as 10.
 

### 2024-03-23 src/data_prep/getting_the_data.R

@@ -41,5 +41,6 @@ movie_data <- Reduce(function(x, y) left_join(x, y, by = join_column), data_sets
 #Awesome! Now we have running code that builds an entire dataframe from seperate ones.
 
 #now let's store the data
+dir.create("data")
 write_csv(movie_data, "data/movie_data.csv")
 

### 2024-03-23 gen/paper/paper.Rmd
added descriptives of the dataset to the paper

--- 2024-03-21 gen/paper/paper.Rmd
@@
 |------------------|------------------------------------------------------------------------------------------------------------------------------------------------------------------|------------------------|
-| Average Rating   | The average rating on IMBd per title of a given movie or series.
+| Average Rating   | The average rating on IMDb per title of a given movie or series.
 | Dependent Variable     |
@@
 | Title            | The title is the given title of any unique movie or series                                                                                                       | Fixed Effect           |
-| 5 Year Window    | The 5 year windown (or ' slide_window_5' indicates between what 5 year window a movie or series belongs to.
-For example a movie from 2003 belonging to 2000-2004 | Split Varible          |
+| 5 Year Window    | The 5 year window (or ' slide_window_5' indicates between what 5 year window a movie or series belongs to.
+For example a movie from 2003 belonging to 2000-2004 | Split Variable          |
+
+### Descriptives
+The data set contains of 70087 films, of which 60246 are movies and 9841 are series.
+These films have on average a rating of 6.3, with 10 being the highest and 1 being the lowest.
+After removing the votes to all being above 100, the average number of votes on a film became 7146.
+When looking at the years, the most amount of films were released on IMDb in 2019, with 2586 films.
+Also when comparing the 5 year range of films released,2015 to 2019 had the most films released, with 11353 films.
+Looking at the runtime of the films, on average a film is 101 minutes long.
 
@@
 
-The average IMBd rating is used as the outcome variable for the
+The average IMDb rating is used as the outcome variable for the
 analysis. However, this average rating is influenced by the number of

### 2024-03-24 src/analysis/regression_analysis.Rmd
added descriptives to data_prepRMD and fixed a bit of the descriptives structure

--- 2024-03-22 src/analysis/regression_analysis.Rmd
@@
 ```{r plotting results}
-coefplot(fixed_tth_model)
+#getting the coefficients
+list_of_coeficients <- coef(fixed_tth_model)
+#getting
+list_of_standard_deviations <- se(fixed_tth_model)
+
+# Pivot coefficients longer
+list_of_coeficients_long <- list_of_coeficients %>%
+  select(!c(sample.var, id)) %>%
+  pivot_longer(cols = c(-sample), names_to = "genre", values_to = "coef_value")
+
+# Pivot standard deviations longer
+list_of_standard_deviations_long <- list_of_standard_deviations %>%
+  select(!c(sample.var, id)) %>%
+  pivot_longer(cols = -sample, names_to = "genre", values_to = "std_dev_value")
+
+graph_data <- left_join(list_of_coeficients_long, list_of_standard_deviations_long, by = c("sample", "genre"))
+
+#confidence level, let's say 95%
+conf_level <- 0.95
+z_value <- qnorm((1 + conf_level) / 2)
+
+graph_data <- graph_data %>%
+  drop_na(coef_value) %>%
+  mutate(   lower_ci = coef_value - z_value * std_dev_value,
+    upper_ci = coef_value + z_value * std_dev_value,
+    p_threshold = coef_value / std_dev_value,
+    p_significance = ifelse(p_threshold > 1.96, 1, 0))
+
+ggplot(graph_data, aes(x = sample, y = coef_value, color = factor(p_significance))) +
+  geom_point() +
+  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2) +
+  scale_color_manual(values = c("red", "green")) +
+  xlab("Estimates") + ylab("Years") +
+  facet_wrap(~ genre)
 ```
@@
 There are also speaks in genres like war, where it seems to be falling in and out of favor.
-```{r}
 
+```{r saving the doc}
+#insert pdf knit path
 ```

### 2024-03-24 src/data_generation/getting_the_data.R
added data_generation folder

@@ -1,0 +1,45 @@
+#The retrival of this data set sometimes runs into some trouble with varification.
+#So, remember to turn on your university VPN !
+
+library(tidyverse)
+
+Data_Source <- list(
+  "https://datasets.imdbws.com/title.ratings.tsv.gz",
+  "https://datasets.imdbws.com/title.episode.tsv.gz",
+  "https://datasets.imdbws.com/title.akas.tsv.gz",
+  "https://datasets.imdbws.com/title.basics.tsv.gz"
+)
+
+# Loop through each URL in the list
+for (url in Data_Source) {
+        file_name <- gsub('.*/title\\.(.*).tsv.gz', '\\1', url) # Extract the file name from the URL
+        download.file(url, destfile = file_name, mode = "wb") # Download the file
+        assign(file_name, read_tsv(file_name)) # Read the downloaded file into R
+        file.remove(file_name) # Remove the downloaded file
+}
+
+#let's merge some datasets! 
+#Please take a close look at all the data sets. Do you see how they all have a label 'tconst"? that is awesome because it allows us to merge the data sets.
+# however, as you look even more closely you see that in the data frame akas, where the label is titleId
+#let's fix that label name. Note that there are alterenative (shorter!) ways to do this.
+akas <- akas %>%
+  mutate(tconst = titleId) %>%
+  select(-titleId)
+
+episode <- episode %>%
+  mutate(across(episodeNumber, as.numeric)) %>% 
+  mutate(across(seasonNumber, as.numeric))
+
+#For example, let's merge rating (our dv) with basics (one of our iv's)
+#Data_set <- left_join(ratings, basics, by = "tconst")
+#while this was nice, we need a larger scale operalization.
+
+data_sets <- list(ratings, basics, episode, akas)
+join_column <- "tconst"
+movie_data <- Reduce(function(x, y) left_join(x, y, by = join_column), data_sets)
+
+#Awesome! Now we have running code that builds an entire dataframe from seperate ones.
+
+#now let's store the data
+dir.create("data")
+write_csv(movie_data, "data/movie_data.csv")

### 2024-03-24 src/analysis/regression_analysis.Rmd
saved plots, changed paths

--- 2024-03-22 src/analysis/regression_analysis.Rmd
@@
 # Let's run our analysis! 
-## And see how genre prefferences as inferred from average ratings evolve over time
+## And see how genre preferences as inferred from average ratings evolve over time
 
@@
 ```{r include=FALSE}
-mdc <- read_csv("../data_prep/movie_data_cleaned.csv")
+mdc <- read_csv("../../data/movie_data_cleaned.csv")
 ```

### 2024-03-24 src/data_prep/data_prep.Rmd
saved plots, changed paths

--- 2024-03-22 src/data_prep/data_prep.Rmd
@@
 ```{r reformatting the data, message=FALSE, warning=FALSE, include=FALSE}
-movie_data <- read_csv("movie_data.csv")
+movie_data <- read_csv("../../data/movie_data.csv")
 
@@
 
+```{r directory, echo=FALSE, warning=FALSE}
+# Create a directory and path to save the plots in
+dir.create("gen/data_prep/output/figure", recursive = T)
+path <- "../../gen/data_prep/output/figure/"
+```
+
 ```{r DV plots, echo=FALSE, message=FALSE, warning=FALSE}
@@
   theme_minimal()
+
+ggsave(filename = "Distribution_averageRating_int1.pdf", plot = last_plot(), device = "pdf", path = path)
 ```
@@
   scale_x_continuous(breaks = seq(0, 10, by = 0.5), limits = c(0, 10), labels = scales::number_format(accuracy = 0.1)) +
-  labs(x = "averageRating", y = "Frequency") +
+  labs(title = "Distribution of averageRating",
+       x = "averageRating", y = "Frequency") +
   theme_minimal()
+
+ggsave(filename = "Distribution_averageRating_int0.5.pdf", plot = last_plot(), device = "pdf", path = path)
 ```
@@
   theme_minimal()
+
+ggsave(filename = "Distribution_numVotes.pdf", plot = last_plot(), device = "pdf", path = path)
 
@@
   theme_minimal()
+
+ggsave(filename = "Distribution_numVotes_below100.pdf", plot = last_plot(), device = "pdf", path = path)
 ```
@@
 Therefore, we construct a window that captures 5 years of viewer patterns.
-Because we do not know how these averRating votes dynamicly evolve over time (for series), we assume that the yearStart is the year in which the most number of votes (numVotes) are generated.
+Because we do not know how these averRating votes dynamically evolve over time (for series), we assume that the yearStart is the year in which the most number of votes (numVotes) are generated.
 This is logical, because if the average rating is positive the series will be continued, and if the reviews are negative the series will be likely to be discontinued.
@@
 Good.
-But before we can continue we have to do some 'eye-conemetrics' and show if there might be data pattern before we run our analysis.
+But before we can continue we have to do some 'eye-econometric' and show if there might be data pattern before we run our analysis.
 First, we look at how number of votes and rating behave for each genre.
@@
   facet_wrap(~genres)
+
+ggsave(filename = "averageRating_x_numVotes_by_genre.pdf", plot = last_plot(), device = "pdf", path = path)
 ```
 
-As you can see there is only a very small patern there.
+As you can see there is only a very small pattern there.
 Typically, very few votes lead to all types of values, including extreme ones.
-However, as the number of votes seem to increase this extreme pattern decresaes slightly.
+However, as the number of votes seem to increase this extreme pattern decreases slightly.
 This means that the number of votes continues to be relevant for our analysis and may even bias our results.
@@
   facet_wrap(~genres)
+
+ggsave(filename = "averageRating_frequency_by_genre.pdf", plot = last_plot(), device = "pdf", path = path)
 ```
 
-As you can see, most of the genres appear to have some normal distribution going on. This is great! let's look at it with a qq plot to confirm our enthousiasm.
+As you can see, most of the genres appear to have some normal distribution going on. This is great! let's look at it with a qq plot to confirm our enthusiasm.
 
@@
   facet_wrap(~genres)
+
+ggsave(filename = "averageRating_qq_plot.pdf", plot = last_plot(), device = "pdf", path = path)
 ```
@@
   ggtitle("Residuals vs. Fitted Values")
+
+ggsave(filename = "averageRating_homoscedasticity.pdf", plot = last_plot(), device = "pdf", path = path)
 ```
@@
   ggtitle("Residuals vs. Index")
+
+ggsave(filename = "averageRating_independence.pdf", plot = last_plot(), device = "pdf", path = path)
 ```
@@
   facet_wrap(~genres)
+
+ggsave(filename = "averageRating_linearity.pdf", plot = last_plot(), device = "pdf", path = path)
 ```
@@
 ```{r save file}
-write_csv(movie_data, "movie_data_cleaned.csv")
+write_csv(movie_data, "../../data/movie_data_cleaned.csv")
 ```

### 2024-03-24 src/data_prep/getting_the_data.R

@@ -1,4 +1,4 @@
-#The retrival of this data set sometimes runs into some trouble with varification.
+#The retrieval of this data set sometimes runs into some trouble with verification.
 #So, remember to turn on your university VPN !
 
 library(tidyverse)
@@ -10,18 +10,22 @@ Data_Source <- list(
   "https://datasets.imdbws.com/title.basics.tsv.gz"
 )
 
+# Create a directory and path to temporarily store the downloaded data
+dir.create("gen/data_prep/temp", recursive = T)
+path <- "gen/data_prep/temp/"
+
 # Loop through each URL in the list
 for (url in Data_Source) {
         file_name <- gsub('.*/title\\.(.*).tsv.gz', '\\1', url) # Extract the file name from the URL
-        download.file(url, destfile = file_name, mode = "wb") # Download the file
-        assign(file_name, read_tsv(file_name)) # Read the downloaded file into R
-        file.remove(file_name) # Remove the downloaded file
+        download.file(url, destfile = paste0(path, file_name), mode = "wb") # Download the file
+        assign(file_name, read_tsv(paste0(path, file_name))) # Read the downloaded file into R
+        file.remove(paste0(path, file_name)) # Remove the downloaded file
 }
 
 #let's merge some datasets! 
 #Please take a close look at all the data sets. Do you see how they all have a label 'tconst"? that is awesome because it allows us to merge the data sets.
 # however, as you look even more closely you see that in the data frame akas, where the label is titleId
-#let's fix that label name. Note that there are alterenative (shorter!) ways to do this.
+#let's fix that label name. Note that there are alternative (shorter!) ways to do this.
 akas <- akas %>%
   mutate(tconst = titleId) %>%
   select(-titleId)
@@ -32,14 +36,15 @@ episode <- episode %>%
 
 #For example, let's merge rating (our dv) with basics (one of our iv's)
 #Data_set <- left_join(ratings, basics, by = "tconst")
-#while this was nice, we need a larger scale operalization.
+#while this was nice, we need a larger scale operationalization.
 
 data_sets <- list(ratings, basics, episode, akas)
 join_column <- "tconst"
 movie_data <- Reduce(function(x, y) left_join(x, y, by = join_column), data_sets)
 
-#Awesome! Now we have running code that builds an entire dataframe from seperate ones.
+#Awesome! Now we have running code that builds an entire data frame from separate ones.
 
 #now let's store the data
[…]

### 2024-03-24 gen/paper/paper.Rmd
added figures to paper

--- 2024-03-23 gen/paper/paper.Rmd
@@
 |------------------|------------------------------------------------------------------------------------------------------------------------------------------------------------------|------------------------|
-| Average Rating   | The average rating on IMDb per title of a given movie or series.
+| Average Rating   | The average rating on IMBd per title of a given movie or series.
 | Dependent Variable     |
@@
 | Title            | The title is the given title of any unique movie or series                                                                                                       | Fixed Effect           |
-| 5 Year Window    | The 5 year window (or ' slide_window_5' indicates between what 5 year window a movie or series belongs to.
-For example a movie from 2003 belonging to 2000-2004 | Split Variable          |
-
-### Descriptives
-The data set contains of 70087 films, of which 60246 are movies and 9841 are series.
-These films have on average a rating of 6.3, with 10 being the highest and 1 being the lowest.
-After removing the votes to all being above 100, the average number of votes on a film became 7146.
-When looking at the years, the most amount of films were released on IMDb in 2019, with 2586 films.
-Also when comparing the 5 year range of films released,2015 to 2019 had the most films released, with 11353 films.
-Looking at the runtime of the films, on average a film is 101 minutes long.
+| 5 Year Window    | The 5 year windown (or ' slide_window_5' indicates between what 5 year window a movie or series belongs to.
+For example a movie from 2003 belonging to 2000-2004 | Split Varible          |
 
@@
 
-The average IMDb rating is used as the outcome variable for the
+The average IMBd rating is used as the outcome variable for the
 analysis. However, this average rating is influenced by the number of
@@
 All assumptions associated with regression were checked via a visual
-inspection. Only linearity appeared to be satisfied.
+inspection. Only normality appeared to be satisfied.
 
 ```{r Normality, echo=FALSE, warning=FALSE}
-#insert pdf
-
+knitr::include_graphics("../../gen/data_prep/output/figure/averageRating_frequency_by_genre.pdf")
 ```
@@
 
-```{r}
-#insert pdf
+```{r plots, echo=FALSE}
+knitr::include_graphics("../../gen/data_prep/output/figure/averageRating_homoscedasticity.pdf")
+knitr::include_graphics("../../gen/data_prep/output/figure/averageRating_independence.pdf")
 ```
@@
 ```{r}
-#insert pdf
+knitr::include_graphics("../../gen/data_prep/output/figure/averageRating_linearity.pdf")
 ```
@@
 ```{r}
-#insert pdf of results graph with colored dots
+knitr::include_graphics("../../gen/analysis/output/figure/plotted_results_regression_analysis.pdf")
 ```

### 2024-03-24 src/analysis/regression_analysis.Rmd
added figures to paper

@@
 
-```{r plotting results}
+```{r plotting results, warning=FALSE}
 #getting the coefficients
@@
 
+dir.create("../../gen/analysis/output/figure", recursive = T)
+ggsave(filename = "plotted_results_regression_analysis.pdf", plot = last_plot(), device = "pdf", path = "../../gen/analysis/output/figure/")
 ```

### 2024-03-24 src/data_prep/getting_the_data.R
added the gen storage folders

@@ -1,46 +1,0 @@
-#The retrival of this data set sometimes runs into some trouble with varification.
-#So, remember to turn on your university VPN !
-
-library(tidyverse)
-
-Data_Source <- list(
-  "https://datasets.imdbws.com/title.ratings.tsv.gz",
-  "https://datasets.imdbws.com/title.episode.tsv.gz",
-  "https://datasets.imdbws.com/title.akas.tsv.gz",
-  "https://datasets.imdbws.com/title.basics.tsv.gz"
-)
-
-# Loop through each URL in the list
-for (url in Data_Source) {
-        file_name <- gsub('.*/title\\.(.*).tsv.gz', '\\1', url) # Extract the file name from the URL
-        download.file(url, destfile = file_name, mode = "wb") # Download the file
-        assign(file_name, read_tsv(file_name)) # Read the downloaded file into R
-        file.remove(file_name) # Remove the downloaded file
-}
-
-#let's merge some datasets! 
-#Please take a close look at all the data sets. Do you see how they all have a label 'tconst"? that is awesome because it allows us to merge the data sets.
-# however, as you look even more closely you see that in the data frame akas, where the label is titleId
-#let's fix that label name. Note that there are alterenative (shorter!) ways to do this.
-akas <- akas %>%
-  mutate(tconst = titleId) %>%
-  select(-titleId)
-
-episode <- episode %>%
-  mutate(across(episodeNumber, as.numeric)) %>% 
-  mutate(across(seasonNumber, as.numeric))
-
-#For example, let's merge rating (our dv) with basics (one of our iv's)
-#Data_set <- left_join(ratings, basics, by = "tconst")
-#while this was nice, we need a larger scale operalization.
-
-data_sets <- list(ratings, basics, episode, akas)
-join_column <- "tconst"
-movie_data <- Reduce(function(x, y) left_join(x, y, by = join_column), data_sets)
-
-#Awesome! Now we have running code that builds an entire dataframe from seperate ones.
-
-#now let's store the data
-dir.create("data")
-write_csv(movie_data, "data/movie_data.csv")
-

### 2024-03-24 src/data_prep/data_prep.Rmd
added image saving

--- 2024-03-23 src/data_prep/data_prep.Rmd
@@
 ```{r reformatting the data, message=FALSE, warning=FALSE, include=FALSE}
-movie_data <- read_csv("data/movie_data.csv")
+movie_data <- read_csv("movie_data.csv")
 
@@
 The mean of the averageRating variable is 6.6. 
-
-```{r DV scale, echo=FALSE}
-Okay. So the scale is okay BUT remember that these are AVERAGE ratings, and that on average ratings 1 and 10 are quite extreme and frankly, unrealistic.
-
-let's visualize how ratings are distributed
+Okay. So the scale is okay BUT remember that these are AVERAGE ratings, and that on average ratings 1 and 10 are quite extreme and frankly, unrealistic. let's visualize how ratings are distributed
 
 ```{r DV plots, echo=FALSE, message=FALSE, warning=FALSE}
-ggplot((movie_data), aes(x = averageRating)) +
+distribution_of_average_ratings <- ggplot((movie_data), aes(x = averageRating)) +
   geom_histogram(binwidth = 1, fill = "darkorange", color = "black") +
@@
   theme_minimal()
+
+ggsave("../../gen/data_preparation/distribution_of_average_ratings.png", distribution_of_average_ratings)
+
+distribution_of_average_ratings
 ```
@@
 ```{r echo=FALSE, message=FALSE, warning=FALSE}
-ggplot(movie_data, aes(x = averageRating)) +
+distribution_of_average_ratings_unrounded <- ggplot(movie_data, aes(x = averageRating)) +
   geom_histogram(binwidth = 0.1, fill = "orange", color = "black") +
@@
   theme_minimal()
+
+ggsave("../../gen/data_preparation/distribution_of_average_ratings_unrounded.png", distribution_of_average_ratings_unrounded)
+
+distribution_of_average_ratings_unrounded
 ```
@@
 ```{r Plot DV and numVotes, echo=FALSE, message=FALSE, warning=FALSE}
-ggplot(movie_data, aes(x = numVotes)) +
+distribution_of_number_of_votes <- ggplot(movie_data, aes(x = numVotes)) +
   geom_dotplot(fill = "darkorange", color = "black", binwidth = 500) +
@@
 print(table(movie_data$numVotes_group))
+
+ggsave("../../gen/data_preparation/distribution_of_number_of_votes.png", distribution_of_number_of_votes)
+
+distribution_of_number_of_votes
 ```
@@
 
-ggplot(below_100, aes(x = numVotes)) +
+distribution_of_number_of_votes_below_10 <-  ggplot(below_100, aes(x = numVotes)) +
   geom_histogram() +
@@
   theme_minimal()
+
+ggsave("../../gen/data_preparation/distribution_of_number_of_votes_below_10.png", distribution_of_number_of_votes_below_10)
+
+distribution_of_number_of_votes_below_10
 ```
@@
   count()
+
 ```
@@
   mutate(genres = as.factor(genres))
+
 ```
@@
 ```{r echo=FALSE}
-ggplot(movie_data, aes(x = numVotes, y = averageRating, color= genres)) +
+number_of_votes_vs_average_rating <- ggplot(movie_data, aes(x = numVotes, y = averageRating, color= genres)) +
   geom_point() + 
   facet_wrap(~genres)
+
+ggsave("../../gen/data_preparation/number_of_votes_vs_average_rating.png", number_of_votes_vs_average_rating)
+
+number_of_votes_vs_average_rating
 ```
@@
 ```{r echo=FALSE}
-ggplot(movie_data, aes(averageRating, color= genres))+
+number_of_votes_distributions_per_genre <- ggplot(movie_data, aes(averageRating, color= genres))+
   geom_bar() +
   facet_wrap(~genres)
+
+ggsave("../../gen/data_preparation/number_of_votes_distributions_per_genre.png", number_of_votes_distributions_per_genre)
+
+number_of_votes_distributions_per_genre
 ```
@@
 ```{r echo=FALSE}
-ggplot(movie_data, aes(sample = averageRating, color = genres)) +
+qq_normality <- ggplot(movie_data, aes(sample = averageRating, color = genres)) +
   stat_qq() +
   facet_wrap(~genres)
+
+ggsave("../../gen/data_preparation/qq_normality.png", qq_normality)
+
+qq_normality
 ```
@@
 # Plot residuals versus fitted values
-ggplot(plot_data, aes(x = Fitted_Values, y = Residuals)) +
+homoskedacity <- ggplot(plot_data, aes(x = Fitted_Values, y = Residuals)) +
   geom_point() +
@@
   ggtitle("Residuals vs. Fitted Values")
+
+ggsave("../../gen/data_preparation/homoskedacity.png", homoskedacity)
+
+homoskedacity
+
 ```
@@
 # Plot residuals versus index
-ggplot(plot_data, aes(x = Index, y = Residuals)) +
+independence <- ggplot(plot_data, aes(x = Index, y = Residuals)) +
   geom_point() +
@@
   ggtitle("Residuals vs. Index")
+
+ggsave("../../gen/data_preparation/independence.png", independence)
+
+independence
+
 ```
@@
 ```{r echo=FALSE}
-ggplot(movie_data, aes(x = slide_window_5, y = averageRating)) +
+linearity <- ggplot(movie_data, aes(x = slide_window_5, y = averageRating)) +
   geom_point() +
   facet_wrap(~genres)
+
+ggsave("../../gen/data_preparation/linearity.png", linearity)
+
+linearity
 ```

### 2024-03-24 gen/paper/paper.Rmd
fixed graph retrieval

--- 2024-03-24 gen/paper/paper.Rmd
@@
   over time
-author: "Team 1 - Timo Philipse, Bram Teunissen, Rodrigo Pačeko Rudzājs, Dian de Ridder
-  & Linda van den Boogaart"
-output:
-  pdf_document: default
-  html_document: default
+author: "Team 1 - Timo Philipse, Bram Teunissen, Rodrigo Pačeko Rudzājs, Dian de Ridder & Linda van den Boogaart"
+output: pdf_document
 editor_options:
@@
 All assumptions associated with regression were checked via a visual
-inspection. Only linearity appeared to be satisfied.
+inspection. Only normality appeared to be satisfied.
 
-```{r Normality, echo=FALSE, warning=FALSE}
-#insert pdf
+```{r echo=FALSE, warning=FALSE}
+library(knitr)
+
+knitr::include_graphics("../../gen/data_preparation/qq_normality.png")
 
@@
 
-```{r}
-#insert pdf
+```{r echo=FALSE}
+knitr::include_graphics("../../gen/data_preparation/homoskedacity.png")
+```
+```{r echo=FALSE}
+knitr::include_graphics("../../gen/data_preparation/independence.png")
 ```
@@
 
-```{r}
-#insert pdf
+```{r echo=FALSE}
+knitr::include_graphics("../../gen/data_preparation/linearity.png")
 ```
@@
 
-```{r}
-#insert pdf of results graph with colored dots
-```
-
 The results indicated that there are different genre preferences over
@@
 reality-tv, news, and war.
+
+```{r echo=FALSE}
+knitr::include_graphics("../../gen/data_analysis/results_plot.png")
+```
 
@@
 analysis results become more reliable.
+
+```{r saving}
+library(rmarkdown)
+
+render(input = "../../gen/paper/paper.Rmd",
+       output_format = "pdf_document",
+       output_file = "../../gen/paper/paper.pdf")
+```

### 2024-03-24 src/analysis/regression_analysis.Rmd
fixed graph retrieval

--- 2024-03-24 src/analysis/regression_analysis.Rmd
@@
+---
+title: "regression analysis"
+author: "Team 1 Data Prep"
+date: "2024-03-24"
+output: pdf_document
+---
+
 # Let's run our analysis! 
-## And see how genre preferences as inferred from average ratings evolve over time
+## And see how genre prefferences as inferred from average ratings evolve over time
 
-```{r libraries, message=FALSE, warning=FALSE, include=FALSE}
+```{r message=FALSE, warning=FALSE, include=FALSE}
 library(tidyverse)
 library(fixest)
-library(tidyr)
 library(skimr)
@@
 library(pdftools)
+library(rmarkdown)
 ```
@@
 Let's start with loading the data 
-```{r include=FALSE}
+```{r retrieving data, include=FALSE}
 mdc <- read_csv("../../data/movie_data_cleaned.csv")
@@
                       split = ~ slide_window_5)
-summary(simple_model)
+etable(simple_model)
 ```
@@
 
-```{r echo=FALSE}
+```{r skeleton model + titleType fixed effect, echo=FALSE, warning=FALSE}
 fixed_type_model <- feols(averageRating ~ drama + romance + war + crime + thriller+ history + comedy + fantasy + adventure + mystery + biography + action + scifi + western + horror + sport + documentary + musical + filmnoir + animation + adult + gameshow + realitytv + talkshow + short + news | titleType,
@@
 
-summary(fixed_type_model)
+etable(fixed_type_model)
 ```
@@
 But let's check our R-squared to be sure.
-
-```{r echo=FALSE}
-etable(simple_model)
-```
-
-```{r echo=FALSE}
-etable(fixed_type_model)
-```
 
@@
 
-```{r include=FALSE}
+```{r model + clustered errors, include=FALSE}
 fixed_tt_model <- feols(averageRating ~ drama + romance + war + crime + thriller+ history + comedy + fantasy + adventure + mystery + biography + action + scifi + western + horror + sport + documentary + musical + filmnoir + animation + adult + gameshow + realitytv + talkshow + short + news | titleType,
@@
                                 split = ~ slide_window_5)
+
+etable(fixed_tt_model)
 ```
@@
 
-```{r assumptions, echo=FALSE}
+```{r model + hetrogeinity adjustement, echo=FALSE}
 
@@
 
-```{r plotting results}
+```{r plotting results, echo=FALSE}
 #getting the coefficients
@@
 
-ggplot(graph_data, aes(x = sample, y = coef_value, color = factor(p_significance))) +
+results_plot <- ggplot(graph_data, aes(x = sample, y = coef_value, color = factor(p_significance))) +
   geom_point() +
@@
   xlab("Estimates") + ylab("Years") +
-  facet_wrap(~ genre)
+  facet_wrap(~ genre) + theme_minimal()
 
+ggsave("../../gen/data_analysis/results_plot.png", results_plot)
+
+results_plot
 ```
+As you can see from the plot some genres, such as romance, are largely significant are nicely consistent over the years.
+However, genres such as game-shows or news (which only rose after the 2000's) do not have observations for all years and the observations that are there are remarkably volatile given their large confidence intervals.
+
+Additionally, some genres are never significant, e.g., sports and thriller.
+While others become significant and never stop, e.g., history.
+There are also speaks in genres like war, where it seems to be falling in and out of favor.
 
 ```{r saving the doc}
-#insert pdf knit path
+render("../../src/analysis/regression_analysis.Rmd",
+       output_format = "pdf_document",
+       "../../gen/data_analysis/regression_analysis.pdf")
 ```

### 2024-03-24 src/data_prep/data_prep.Rmd
fixed graph retrieval

@@
+---
+title: "data_preparation"
+author: "Team 1 Data Prep"
+date: "2024-03-24"
+output: pdf_document
+---
+
 # Cleaning the Data
@@
 
-```{r libraries, message=FALSE, warning=FALSE, include=FALSE}
+```{r message=FALSE, warning=FALSE, include=FALSE}
 library(tidyverse)
@@
 library(stringr)
+library(rmarkdown)
 ```
@@
 
-```{r echo=FALSE, message=FALSE, warning=FALSE}
+```{r distribution_of_average_ratings_unrounded, echo=FALSE, message=FALSE, warning=FALSE}
 distribution_of_average_ratings_unrounded <- ggplot(movie_data, aes(x = averageRating)) +
@@
 
-```{r Plot DV and numVotes, echo=FALSE, message=FALSE, warning=FALSE}
+```{r distribution_of_number_of_votes, echo=FALSE, message=FALSE, warning=FALSE}
 distribution_of_number_of_votes <- ggplot(movie_data, aes(x = numVotes)) +
@@
 
-```{r Filtering DV, echo=FALSE, message=FALSE, warning=FALSE}
+```{r distribution_of_number_of_votes_below_10, echo=FALSE, message=FALSE, warning=FALSE}
 below_100 <- movie_data %>%
@@
 
-```{r echo=FALSE}
+```{r number_of_votes_vs_average_rating, echo=FALSE}
 number_of_votes_vs_average_rating <- ggplot(movie_data, aes(x = numVotes, y = averageRating, color= genres)) +
@@
 Let's see how the actual ratings are then distributed across genres
-```{r echo=FALSE}
+```{r number_of_votes_distributions_per_genre, echo=FALSE}
 number_of_votes_distributions_per_genre <- ggplot(movie_data, aes(averageRating, color= genres))+
@@
 
-```{r echo=FALSE}
+```{r qq_normality, echo=FALSE}
 qq_normality <- ggplot(movie_data, aes(sample = averageRating, color = genres)) +
@@
 
-```{r echo=FALSE}
+```{r homoskedacity, echo=FALSE}
 residuals <- movie_data$averageRating - mean(movie_data$averageRating)
@@
 
-```{r echo=FALSE}
+```{r independence, echo=FALSE}
 # Calculate residuals
@@
 
-Linearity looks chaotic but okay.
+Indepdence looks chaotic but okay.
 It may be a little smaller on the left and increases to the right but this is very little.
@@
 
-```{r echo=FALSE}
+```{r linearity, echo=FALSE}
 linearity <- ggplot(movie_data, aes(x = slide_window_5, y = averageRating)) +
@@
 ```
+
 After all the filtering, we have 70087 films left in our data set. From this number, 60246 are movies and 9841 are series. The resulting standard deviation for the total of films is 1.12. 
@@
 
-```{r save file}
-write_csv(movie_data, "data/movie_data_cleaned.csv")
+```{r save file, echo=TRUE}
+write_csv(movie_data, "../../data/movie_data_cleaned.csv")
 ```

### 2024-03-24 src/analysis/regression_analysis.Rmd
moved shiny app and changed data path regression_analysis

@@
 ```{r saving the doc}
+write_csv(graph_data, "../../data/graph_data.csv")
+
 render("../../src/analysis/regression_analysis.Rmd",

### 2024-03-24 src/data_prep/data_prep.Rmd
removed typos

@@
 Good.
-But before we can continue we have to do some 'eye-conemetrics' and show if there might be data pattern before we run our analysis.
+But before we can continue we have to do some 'eye-econemetrics' and show if there might be data pattern before we run our analysis.
 First, we look at how number of votes and rating behave for each genre.
@@
 
-As you can see there is only a very small patern there.
+As you can see there is only a very small pattern there.
 Typically, very few votes lead to all types of values, including extreme ones.
-However, as the number of votes seem to increase this extreme pattern decresaes slightly.
+However, as the number of votes seem to increase this extreme pattern decreases slightly.
 This means that the number of votes continues to be relevant for our analysis and may even bias our results.
@@
 
-As you can see, most of the genres appear to have some normal distribution going on. This is great! let's look at it with a qq plot to confirm our enthousiasm.
+As you can see, most of the genres appear to have some normal distribution going on. This is great! let's look at it with a qq plot to confirm our enthusiasm.
 

### 2024-03-24 src/data_generation/getting_the_data.R

@@ -1,4 +1,4 @@
-#The retrival of this data set sometimes runs into some trouble with varification.
+#The retrieval of this data set sometimes runs into some trouble with verification.
 #So, remember to turn on your university VPN !
 
 library(tidyverse)
@@ -21,7 +21,7 @@ for (url in Data_Source) {
 #let's merge some datasets! 
 #Please take a close look at all the data sets. Do you see how they all have a label 'tconst"? that is awesome because it allows us to merge the data sets.
 # however, as you look even more closely you see that in the data frame akas, where the label is titleId
-#let's fix that label name. Note that there are alterenative (shorter!) ways to do this.
+#let's fix that label name. Note that there are alternative (shorter!) ways to do this.
 akas <- akas %>%
   mutate(tconst = titleId) %>%
   select(-titleId)
@@ -32,13 +32,13 @@ episode <- episode %>%
 
 #For example, let's merge rating (our dv) with basics (one of our iv's)
 #Data_set <- left_join(ratings, basics, by = "tconst")
-#while this was nice, we need a larger scale operalization.
+#while this was nice, we need a larger scale operationalization.
 
 data_sets <- list(ratings, basics, episode, akas)
 join_column <- "tconst"
 movie_data <- Reduce(function(x, y) left_join(x, y, by = join_column), data_sets)
 
-#Awesome! Now we have running code that builds an entire dataframe from seperate ones.
+#Awesome! Now we have running code that builds an entire data frame from separate ones.
 
 #now let's store the data
 dir.create("data")

### 2024-03-25 gen/paper/paper.Rmd
paper knits

@@
 author: "Team 1 - Timo Philipse, Bram Teunissen, Rodrigo Pačeko Rudzājs, Dian de Ridder & Linda van den Boogaart"
-output: pdf_document
+output: 
+  pdf_document: {}
 editor_options:
@@
 example, war movies tend to receive higher ratings during world wars
-compared to times of peace. This implies that consumers use these
+compared to times of peace. This may imply that consumers use these
 productions as references to rate them in context of the sign of the
@@
 ratings from consumers, while those produced in the 70s are rated more
-favorably. Overall, the results suggest that managers may face
+favorably. Overall, the results may suggest that managers may face
 challenges in meeting previously set expectations and that these
@@
 has a similar pattern of ingredients. Most movies contain hints of drama
-and romance. Whether it is in a distropian sci-fi survival movie or an
-horror action series. However, the results indicated that these common
-genres are not significantly related to the average ratings. In contrast
-some movies and series do contain unique elements do results in
+and romance, regardless of whether it is in a distropian sci-fi survival movie or an horror action series.
+However, the results indicated that these common genres are not significantly related to the average ratings.
+In contrast some movies and series do contain unique elements do results in
 significant relationships. For example, biographies and animations. This
@@
 In this paper we investigate consumers’ movie and series preferences
-using four of IMDb's datasets containing movie data. First, these
+using four of IMDb's data sets containing movie data. First, these
 
-datasets are loaded, cleaned, inspected, merged and cleaned. Next, the
-data is analyzed using a regression analysis. This regression analysis
-regresses all movie and series genre's against the average rating's over
-a sliding period of 5 years. Additionally, the variables title,
-movieType and time are used as control variables to improve the
-interpret ability of the estimates.
+Data sets are loaded, cleaned, inspected, merged and cleaned. Next, the
+data is analyzed using a regression analysis.
+This method was chosen due to the continuous nature of the dependent variable and the categorical nature of the independent variables.
+The reason why a regression was chosen over the alternative of an ANOVA was due to the size and complexity of the analysis.
+There are 27 genres included as a dependent variable, and are measure over time.
+To include these features into an ANOVA is far more complex compared to a regression analysis.
+
+This regression analysis regresses all movie and series genre's against the average rating's over a sliding period of 5 years.
+Additionally, the variables title, movieType and time are used as control variables to improve the interpret ability of the estimates.
+Additionally, because some of the assumptions were only robustly satisfied, the standard errors were clustered.
+The analysis resulted in a 20 window output, one for each year window.
+
+A note of attention should be, that despite the richness of the data, the interpretation of the results remain descriptive at bests.
+This is because the average movie ratings are not reported over time but are merely a static measure of today's average.
+This implies that a single coefficient is read as "The genre X produced in the year Y is positively/negatively associated with the average movie rating of today."
 
@@
 ### Descriptives
+
 The data set contains of 70087 films, of which 60246 are movies and 9841 are series.
@@
 Also when comparing the 5 year range of films released,2015 to 2019 had the most films released, with 11353 films.
-Looking at the runtime of the films, on average a film is 101 minutes long.
+LAst, when looking at the run time of the films, on average a film is 101 minutes long.
 
@@
 cut-off of a hundred will not be included in the regression analysis.
+
+Please note the average movie rating is a static measure that does not change the dynamics of the rating.
+For example, we can only see today's average rating but not that of 2 hours, 2 days, or even 2 years ago.
 
@@
 because a niche selection of the population may be watching these movies
-in the first place.
+in the first place. Therefore, regardless of the additions of these fixed effects the results of the analysis are correlational at best.
 
@@
 detected. Therefore, a five-year window was created that captures all 
-genre preferences for that period of time.
+genre preferences for that period of time. This window was constructed by grouping all productions in an interval of five years.
 
@@
 
+#### Normality
+
 ```{r echo=FALSE, warning=FALSE}
@@
 knitr::include_graphics("../../gen/data_preparation/qq_normality.png")
-
 ```
@@
 
+#### Homoskedacity
+
 ```{r echo=FALSE}
@@
 ```
+
+#### Independence
+
 ```{r echo=FALSE}
@@
 ```
+
+#### Linearity
 
@@
 out as much as biography and history might.
-The results of this analysis can be, at best, interpreted as correlational 
+
+The results of this analysis can be, at best, interpreted as descriptive 
 given the vast amount of assumptions and potential hidden dangers of 
 sampling biases (e.g., film-noir and war genres). While this has been 
-partially mitigated by loosening some of the underlying assumptions and 
-adding fixed effects, the fact remains that these appear as trend 
+partially mitigated by loosening some of the underlying assumptions (clustering standard errors and selecting a better heterogeneity method) and adding fixed effects, the fact remains that these appear as trend
 observations. Therefore, the results do not necessarily conclude that some 
-genres lead to higher average ratings. However, the results do indicate that 
-there may be preferences over time that may lead to higher average ratings.
+genres lead to higher average ratings. However, the results do indicate that there may be preferences over time that may lead to higher average ratings.
 
@@
 analysis results become more reliable.
-
-```{r saving}
-library(rmarkdown)
-
-render(input = "../../gen/paper/paper.Rmd",
-       output_format = "pdf_document",
-       output_file = "../../gen/paper/paper.pdf")
-```

### 2024-03-25 src/analysis/regression_analysis.Rmd
removed typos
fixed rendering problem

@@
 
-render("../../src/analysis/regression_analysis.Rmd",
-       output_format = "pdf_document",
-       "../../gen/data_analysis/regression_analysis.pdf")
 ```

### 2024-03-25 src/analysis/regression_analysis.Rmd
Finalized the makefile and updated some .r or .rmd

@@
 library(rmarkdown)
+library(tinytex)
+library(latexpdf)
+library(latexdiffr) 
 ```

### 2024-03-25 src/data_generation/getting_the_data.R

@@ -18,28 +18,4 @@ for (url in Data_Source) {
         file.remove(file_name) # Remove the downloaded file
 }
 
-#let's merge some datasets! 
-#Please take a close look at all the data sets. Do you see how they all have a label 'tconst"? that is awesome because it allows us to merge the data sets.
-# however, as you look even more closely you see that in the data frame akas, where the label is titleId
-#let's fix that label name. Note that there are alternative (shorter!) ways to do this.
-akas <- akas %>%
-  mutate(tconst = titleId) %>%
-  select(-titleId)
-
-episode <- episode %>%
-  mutate(across(episodeNumber, as.numeric)) %>% 
-  mutate(across(seasonNumber, as.numeric))
-
-#For example, let's merge rating (our dv) with basics (one of our iv's)
-#Data_set <- left_join(ratings, basics, by = "tconst")
-#while this was nice, we need a larger scale operationalization.
-
-data_sets <- list(ratings, basics, episode, akas)
-join_column <- "tconst"
-movie_data <- Reduce(function(x, y) left_join(x, y, by = join_column), data_sets)
-
-#Awesome! Now we have running code that builds an entire data frame from separate ones.
-
-#now let's store the data
-dir.create("data")
-write_csv(movie_data, "data/movie_data.csv")
+save.image("data/movie_data.RData")

### 2024-03-25 src/data_prep/data_prep.Rmd

@@
 library(rmarkdown)
+library(tinytex)
+library(pdftools)
+library(latexpdf)
+library(latexdiffr) 
 ```

### 2024-03-25 src/data_generation/getting_the_data.R
Will it ever really be final?

@@ -2,6 +2,9 @@
 #So, remember to turn on your university VPN !
 
 library(tidyverse)
+dir.create("data")
+dir.create("data/temp", recursive = T)
+path = "data/temp/"
 
 Data_Source <- list(
   "https://datasets.imdbws.com/title.ratings.tsv.gz",
@@ -13,10 +16,9 @@ Data_Source <- list(
 # Loop through each URL in the list
 for (url in Data_Source) {
         file_name <- gsub('.*/title\\.(.*).tsv.gz', '\\1', url) # Extract the file name from the URL
-        download.file(url, destfile = file_name, mode = "wb") # Download the file
-        assign(file_name, read_tsv(file_name)) # Read the downloaded file into R
-        file.remove(file_name) # Remove the downloaded file
+        download.file(url, destfile = paste0(path, file_name), mode = "wb") # Download the file
+        assign(file_name, read_tsv(paste0(path, file_name))) # Read the downloaded file into R
+        file.remove(paste0(path, file_name)) # Remove the downloaded file
 }
 
-dir.create("data") # Create a directory to save the data
 save.image("data/movie_data.RData")
